---
title: "habitat_data"
author: "Becca Van Hoeck"
date: "12/20/2019"
output: pdf_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
```

02/15/2022 Note: reviewed all code, confirmed joins, and replaced most references to hard-coded column numbers

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(vegan)
```

## Load all habitat data

```{r }

data = read.csv("data/clean_data/sound_habitat_data_2020.csv", header = TRUE)

```

## Summarize each site
- calculate site level average cover (wide and long form)
- plot percent cover
- calculate habitat forming species richness, diversity, and evenness

```{r}
# Average cover by each taxa at site level

# Wide form: for data frame
site_means = data %>% 
  group_by(deploy_num,site) %>%
  summarise(bare = mean(bare), halodule = mean(halodule), zostera = mean(zostera), 
            ruppia= mean(ruppia), algae = mean(algae), oyster = mean(oyster), saltmarsh = mean(saltmarsh),
            other = mean(other))

# Long form: for EDA plots
siteMean_pc = data.frame(gather(site_means, "identity", "perc_cover", -site, -deploy_num))
siteMean_pc$identity = factor(siteMean_pc$identity, levels = c("bare","halodule","oyster","saltmarsh",
                                                               "ruppia", "zostera", "algae", "other"))

ggplot(siteMean_pc, aes(x = perc_cover, y = identity, color = identity))+ theme_bw()+
  geom_point(alpha = .5, position = "jitter")+
  xlab('Percent Cover')+
  ylab('Benthic species identity')+
  theme(axis.title = element_text(size = 14), 
        axis.text = element_text(size = 12), 
        legend.position = "none")


## Benthic species community metrics - excludes algae & other
site_means$richness = apply(site_means[,c("halodule","zostera","ruppia","saltmarsh","oyster")]>0,1,sum) 
site_means$shannonD = diversity(site_means[,c("halodule","zostera","ruppia","saltmarsh","oyster")], "shannon")
site_means$evenness = site_means$shannonD/log(site_means$richness, base = 2)

```

## Summarized by seagrass 
- repeat average cover and metric calculations with seagrass species combined
- plot percent cover combined

```{r}
data = data %>% mutate(seagrass = halodule+zostera+ruppia)

# Wide form: for data frame
site_means_comb = data %>% 
  group_by(deploy_num,site) %>%
  summarise(bare = mean(bare), seagrass = mean(seagrass), algae = mean(algae), 
            oyster = mean(oyster), saltmarsh = mean(saltmarsh), other = mean(other))

# Long form: for plotting
siteMean_pc_comb = data.frame(gather(site_means_comb, "identity", "perc_cover", -site, -deploy_num))
siteMean_pc_comb$identity = factor(siteMean_pc_comb$identity, 
                                   levels = c("bare","seagrass","oyster","saltmarsh","algae","other"))

ggplot(siteMean_pc_comb, aes(x = perc_cover, y = identity, color = identity))+ theme_bw()+
  geom_point(alpha = .5, position = "jitter")+
  xlab('Percent Cover')+
  ylab('Benthic species identity')+
  theme(axis.title = element_text(size = 14), 
        axis.text = element_text(size = 12), 
        legend.position = "none")

# Seagrass species specific cover: for plotting
seagrass_pc = site_means[,c(1,2,4:6)]
seagrass_pc_long = data.frame(gather(seagrass_pc, "identity", "perc_cover", -site, -deploy_num))

ggplot(seagrass_pc_long, aes(x = perc_cover, y = identity, color = identity))+ theme_bw()+
  geom_point(alpha = .5, position = "jitter")+
  xlab('Percent Cover')+
  ylab('Benthic species identity')+
  theme(axis.title = element_text(size = 14), 
        axis.text = element_text(size = 12), 
        legend.position = "none")

## Benthic species community metrics - excludes algae & other
site_means_comb$richness_comb = apply(site_means_comb[,c("seagrass","oyster","saltmarsh")]>0, 1, sum)
site_means_comb$shannonD_comb = diversity(site_means_comb[,c("seagrass","oyster","saltmarsh")], "shannon")
site_means_comb$evenness_comb = site_means_comb$shannonD_comb/log(site_means_comb$richness_comb, base = 2)

```

## Total cover of habitat-forming species
- calculate total cover of habitat-forming species

```{r}
data = data %>% 
  mutate(total_cover = halodule+zostera+ruppia+saltmarsh+oyster+algae+other, 
         habitat = case_when(grepl("Seagrass", site) ~ "seagrass", 
                             grepl("Creek", site) ~ "creek",
                             grepl("Mudflat", site) ~ "mudflat"))

total_cover = data %>%
  group_by(deploy_num, site) %>%
  summarise(total_cover = mean(total_cover)) %>%
  mutate(Habitat = case_when(grepl("Seagrass", site) ~ "Seagrass", 
                             grepl("Creek", site) ~ "Creek",
                             grepl("Mudflat", site) ~ "Mudflat"))

ggplot(total_cover , aes(x = reorder(site, total_cover), y = total_cover, 
                         fill = Habitat, color = Habitat))+theme_bw()+
  geom_col()+ 
  theme(axis.text.x = element_text(angle = -90, hjust = 0, vjust = .3), 
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14))+
  labs(x = "Site", y = "Total Cover Habitat Forming Species")

```

## Seagrass data
- summarizes seagrass avg blade length, max 10 blades, max 25% blades, and avg shoot density
```{r}
seagrass = read.csv("data/raw_data/seagrass_all.csv", header = TRUE)
seagrass$id = paste(seagrass$site, seagrass$Transect, sep = "_")
seagrass_max = read.csv("data/clean_data/seagrass_max_canopy.csv", header = TRUE) #max canopy as calculated in excel

ggplot(seagrass, aes(x = Site_code, y = Length))+ theme_bw()+
  geom_boxplot()+ ylab("Seagrass blade length")+
  theme(axis.title = element_text(size = 14), 
        axis.text = element_text(size = 12))

# # Calculate mean blade length by transect
# seagrass_summary = seagrass %>%
#   group_by(Date, site, Transect) %>%
#   summarise(mean = mean(Length))
# 
# # # add max blade length to df - transect
# # seagrass_summary$max_10 = seagrass_max$mean_10
# # seagrass_summary$max_25perc = seagrass_max$mean_25percent

# Average blade length by site
seagrass_site = seagrass %>%
  group_by(Date, site) %>%
  summarise(avg_blade_length = mean(Length))

# Average Shoot density by site
shoot_data = data %>% 
  filter(canopy.sampled == "yes")
avg_shoot_density = shoot_data %>% 
  group_by(deploy_num, site) %>%
  summarize(avg_shoot_density = mean(shoot.density1_16m2))

# Summarize max canopy by site
# Averages the max of each transect (this is not how the cover is calculated)
max_canopy_site = seagrass_max %>%
  group_by(site) %>%
  summarize(max10 = mean(mean_10))
  
# Put all seagrass summaries together
seagrass_all = left_join(seagrass_site, avg_shoot_density[,c("site","avg_shoot_density")], by = "site")
seagrass_all = left_join(seagrass_all, max_canopy_site[,c("site", "max10")], by = "site")

```

## Community data - summarized by each tow

## - indicates code I've edited to explore trophic level and invertebrate abundances

```{r}
trawl = read.csv("data/raw_data/trawl/summer_trawl_data_2019.csv", header = TRUE)

#trawl summary
tow_time = mean(trawl$Duration_min_sec)
tow_timeSD = sd(trawl$Duration_min_sec)
tow_speed = mean(trawl$Speed_km_hr)
tow_speedSD = sd(trawl$Speed_km_hr)

trawl$Depth_m[43] = 1
trawl$Depth_m = as.numeric(trawl$Depth_m)
tow_depthMin = min(trawl$Depth_m)
tow_depthMax = max(trawl$Depth_m)
tow_depth = mean(trawl$Depth_m)

# catch summary
catch_data = data.frame(trawl[,c(1,3:5,7,13:17,19:67)])
spp_data = catch_data[,11:59]
spp_data[is.na(spp_data)] = 0
spp_data = spp_data[, colSums(spp_data) > 0]
catch_data = cbind(catch_data[,1:10],spp_data)

# species = data.frame(colnames(spp_data))
# write.csv(species, file = "species_list.csv")

catch_long = data.frame(gather(catch_data, "identity", "abund", -Date, -Tow_number,-Site, -Project.Site.Name, 
                               -Habitat, -Distance_m, -Distance_km_speed_duration_calc, -Depth_m, -Temp_C, -Sal_ppt))
catch_long = catch_long %>%
 mutate(std_dist = Distance_m/100, std_abund = abund/std_dist)

std_catch = data.frame(pivot_wider(catch_long,id_cols = 1:10, names_from = "identity",values_from = "std_abund"))

##species_list = read.csv("data/metadata/species_list.csv", header = TRUE)
species_list = read.csv("data/metadata/species_list_v2.csv", header = TRUE)

##catch_long = left_join(catch_long, species_list[,c(2,4:7)], by = c("identity" = "colnames.spp_data.")) 
catch_long = left_join(catch_long, species_list[,c(2,4:6,8,9)], by = c("identity" = "colnames.spp_data.")) 

# Sum replicate trawls
catch_long$Depth_m = as.numeric(catch_long$Depth_m)
## test_catch = catch_long %>%
##   group_by(Project.Site.Name, identity) %>%
##   summarise(habitat = Habitat, guild = guild, guild_secondary = guild_secondary, soniferous = soniferous, 
##             depth_m_avg = mean(Depth_m), temp_avg = mean(Temp_C), sal_avg = mean(Sal_ppt),
##             dist_m_sum = sum(Distance_m), abund_sum = sum(abund))
test_catch = catch_long %>%
  group_by(Project.Site.Name, identity) %>%
  summarise(habitat = Habitat, guild = guild, guild_secondary = guild_secondary, soniferous = soniferous, 
            depth_m_avg = mean(Depth_m), temp_avg = mean(Temp_C), sal_avg = mean(Sal_ppt),
            dist_m_sum = sum(Distance_m), abund_sum = sum(abund),
            trophic_level = trophic_level, phylum = phylum)


test_catch = test_catch %>%
 mutate(std_dist_sum = dist_m_sum/200, std_abund_sum = abund_sum/std_dist_sum)

test_catch = distinct(test_catch)

soniferous = test_catch %>%
  filter(abund_sum > 0)%>%
  group_by(Project.Site.Name, soniferous)%>%
  summarize(soniferous_S = n()) %>%
  filter(soniferous == 'Y')

std_catch_sum = data.frame(pivot_wider(test_catch,id_cols = c(1,3,7:9), 
                                       names_from = "identity",values_from = "std_abund_sum"))
#write.csv(std_catch_sum, "data/clean_data/std_catch_sum.csv")

# Community metrics summed
trawl_metrics = std_catch_sum[,c(1:5)]
trawl_metrics$total_abund_sum = rowSums(std_catch_sum[,6:41])
trawl_metrics$comm_richness_sum = apply(std_catch_sum[,c(6:41)]>0, 1, sum)
trawl_metrics$comm_shannonD_sum = diversity(std_catch_sum[,6:41], "shannon")
trawl_metrics$comm_evenness_sum = trawl_metrics$comm_shannonD_sum/log(trawl_metrics$comm_richness_sum, base = 2)

# Abundance by guild
guild_abund = test_catch %>%
  group_by(Project.Site.Name,guild) %>%
  summarise(guild_abund = mean(std_abund_sum))

guild_abund = pivot_wider(guild_abund, id_cols = 1, names_from = "guild", values_from = "guild_abund")

# Combine trawl metrics
trawl_metrics = left_join(trawl_metrics, guild_abund, by = "Project.Site.Name")
trawl_metrics = left_join(trawl_metrics, soniferous, by = "Project.Site.Name")
trawl_metrics$soniferous[is.na(trawl_metrics$soniferous)] <- "N"
trawl_metrics$soniferous_S[is.na(trawl_metrics$soniferous_S)] <- 0

# Abundance by Secondary guilds
guild2_abund = test_catch %>%
  group_by(Project.Site.Name,guild_secondary) %>%
  summarise(guild2_abund = mean(std_abund_sum))

guild2_abund = pivot_wider(guild2_abund, id_cols = 1, names_from = "guild_secondary", values_from = "guild2_abund")
trawl_metrics = left_join(trawl_metrics, guild2_abund, by = "Project.Site.Name")

# Retain abundances of species of interest
trawl_metrics = left_join(trawl_metrics, std_catch_sum[,c("Project.Site.Name","num_bai_chr","num_ort_chr","num_ops_tau")], by="Project.Site.Name")


### Explore trophic level and invertebrate density
invert_abund = test_catch %>%
  group_by(Project.Site.Name, phylum) %>%
  summarise(phylum_abund = sum(std_abund_sum))
phylum_abund = pivot_wider(invert_abund, id_cols = 1, names_from = "phylum", values_from = "phylum_abund")

# explore correlation before moving forward
test_cor = left_join(phylum_abund,spl_pmHT, by = c("Project.Site.Name" = "site"))
test_cor = left_join(test_cor, toadfish, by = c("Project.Site.Name" = "Site"))
test_cor$ToadCallRate[test_cor$ToadCallRate == "NaN"] = 0

# mean trophic level weighted by abundance?
# (sum(trophic level * abundance)) for each species/total_abund in trawl? 
trophic_by_abund = test_catch %>%
  group_by(Project.Site.Name, identity) %>%
  summarise(trophic_by_abund = trophic_level*std_abund_sum)

avg_trophic = trophic_by_abund %>%
  group_by(Project.Site.Name) %>%
  summarise(sum_trophic = sum(trophic_by_abund, na.rm = TRUE))
  
avg_trophic$avg_trophic = avg_trophic$sum_trophic/trawl_metrics$total_abund_sum

test_cor = left_join(test_cor, avg_trophic, by = "Project.Site.Name")
test_cor$avg_trophic[test_cor$avg_trophic == "NaN"] = 0


cor(test_cor$invertebrate, test_cor$avg_spl_low, method = "pearson")
cor(test_cor$invertebrate, test_cor$avg_spl_high, method = "pearson")
cor(test_cor$invertebrate, test_cor$ToadCallRate, method = "pearson")

cor(test_cor$avg_trophic, test_cor$avg_spl_low, method = "pearson")
cor(test_cor$avg_trophic, test_cor$avg_spl_high, method = "pearson")
cor(test_cor$avg_trophic, test_cor$ToadCallRate, method = "pearson")

# filter to seagrass only: 
test_cor_seagrass = test_cor[13:24,]
cor(test_cor_seagrass$invertebrate, test_cor_seagrass$avg_spl_low, method = "pearson")
cor(test_cor_seagrass$invertebrate, test_cor_seagrass$avg_spl_high, method = "pearson")
cor(test_cor_seagrass$invertebrate, test_cor_seagrass$ToadCallRate, method = "pearson")

cor(test_cor_seagrass$avg_trophic, test_cor_seagrass$avg_spl_low, method = "pearson")
cor(test_cor_seagrass$avg_trophic, test_cor_seagrass$avg_spl_high, method = "pearson")
cor(test_cor_seagrass$avg_trophic, test_cor_seagrass$ToadCallRate, method = "pearson")

```

## Landscape scale habitat data

```{r}

landscapeMetrics = read.csv("data/clean_data/landscape_metrics.csv", header = TRUE)
landscapeMetrics = landscapeMetrics %>%
  mutate(habitat_total = seagrass_area+saltmarsh_area+oyster_area) %>%
  select(-contains(c("sand", "channel","land","shape","mudflat")))


# manually edited nearest_neighbor_results.csv to include site_code
annMetrics = read.csv("data/raw_data/nearest_neighbor_results.csv", header = TRUE)

```

## Temperature data

```{r}

tempST = read.csv("data/clean_data/pmHT_tempAvg.csv", header = TRUE)

```

## Soundscape data

```{r}
# Site names added manually
spl_pmHT = as.data.frame(read.csv("data/clean_data/avg_pmHT_SPL.csv", header = TRUE))

# Toadfish call rates
toadfish = read.csv("data/clean_data/ToadfishCallRate.csv")

# # Add bioacoustic index 
# BI = read.csv("data/clean_data/bioacousticIndex.csv")
```

## Putting it together

```{r}
ecometrics = site_means
ecometrics = left_join(ecometrics, site_means_comb[,c("site","seagrass","richness_comb","shannonD_comb","evenness_comb")], 
                       by = "site")
ecometrics = left_join(ecometrics, total_cover[,c("site","total_cover", "Habitat")], by = "site")
ecometrics = left_join(ecometrics, seagrass_all[,c("site","avg_blade_length","avg_shoot_density","max10")], by =  "site")

#create matching habitat variable to join habitat and trawl data
ecometrics$site_code = c("C7","MF2","SG10","SG12","C2","MF1","SG2","SG4","CB","MFA","SB","SC","C8","MF7","SG6","SG9",
                         "C4","C5","S14","S15","C3","C6","SG1","SG17")
ecometrics = left_join(ecometrics, trawl_metrics, by = c("site_code"="Project.Site.Name"))

ecometrics = left_join(ecometrics, landscapeMetrics, by = c("site_code" = "site"))
ecometrics = left_join(ecometrics, annMetrics[,c("site_code","NNratio","dist2adjPatch","adj_hab_type","richness_landscape")], by = "site_code")
ecometrics = left_join(ecometrics, tempST, by = "site_code")
ecometrics = left_join(ecometrics, spl_pmHT, by = c("site_code" = "site"))
ecometrics = left_join(ecometrics, toadfish, by = c("site_code" = "Site"))

# Convert seagrass canopy NAs to zeros
ecometrics$avg_blade_length[is.na(ecometrics$avg_blade_length)] = 0
ecometrics$avg_shoot_density[is.na(ecometrics$avg_shoot_density)] = 0
ecometrics$max10[is.na(ecometrics$max10)] = 0

ecometrics$ToadCallRate[is.na(ecometrics$ToadCallRate)] = 0

# remove temperature from trawl data
ecometrics = ecometrics %>%
  select(-temp_avg)

# include average depth and salinity for 2 sites with missing data
ecometrics$depth_m_avg[is.na(ecometrics$depth_m_avg)] = mean(ecometrics$depth_m_avg, na.rm = TRUE)
ecometrics$sal_avg[is.na(ecometrics$sal_avg)] = mean(ecometrics$sal_avg, na.rm = TRUE)


```

## Save ecometrics dataframes

```{r}

write.csv(ecometrics, "data/clean_data/ecometrics.csv")

# Filter ecometrics to habitat specific data and save
ecometrics_seagrass = ecometrics %>%
  filter(Habitat == "Seagrass")
ecometrics_creek = ecometrics %>%
  filter(Habitat == "Creek")
ecometrics_mudflat = ecometrics %>%
  filter(Habitat == "Mudflat")

write.csv(ecometrics_seagrass, "data/clean_data/ecometricsSeagrass.csv")
write.csv(ecometrics_creek, "data/clean_data/ecometricsCreek.csv")
write.csv(ecometrics_mudflat, "data/clean_data/ecometricsMudflat.csv")

```




