---
title: "correlation_by_habitat"
author: "Becca Van Hoeck"
date: "2/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load packages

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(gridExtra)
library(MuMIn)

ecometrics = read.csv("data/clean_data/ecometrics.csv")

```

## Explore grouping by habitat type

```{r}
# SPL by Habitat
ggplot(data = ecometrics, aes(x = habitat, y = avg_spl_low))+ theme_bw()+
  geom_boxplot()

splbyhabitat = lm(avg_spl_low ~ habitat, data = ecometrics)
summary(splbyhabitat)
SPLbyHabAOV = aov(splbyhabitat)
TukeyHSD(SPLbyHabAOV)

ggplot(data = ecometrics, aes(x = habitat, y = avg_spl_high))+ theme_bw()+
  geom_boxplot()

splHbyhabitat = lm(avg_spl_high ~ habitat, data = ecometrics)
summary(splHbyhabitat)
SPLHbyHabAOV = aov(splHbyhabitat)
TukeyHSD(SPLHbyHabAOV)


# # SPL by nearest adj habitat type (landscape) 
# ggplot(data = metricsSG, aes(x = adj_hab_type, y = avg_spl_low))+ theme_bw()+
#   geom_boxplot()
# 
# ggplot(data = metricsSG, aes(x = adj_hab_type, y = avg_spl_high))+ theme_bw()+
#   geom_boxplot()
# 
# ggplot(data = metricsC, aes(x = adj_hab_type, y = avg_spl_low))+ theme_bw()+
#   geom_boxplot()
# 
# ggplot(data = metricsC, aes(x = adj_hab_type, y = avg_spl_high))+ theme_bw()+
#   geom_boxplot()
# 
# ggplot(data = metricsM, aes(x = adj_hab_type, y = avg_spl_low))+ theme_bw()+
#   geom_boxplot()
# 
# ggplot(data = metricsM, aes(x = adj_hab_type, y = avg_spl_high))+ theme_bw()+
#   geom_boxplot()

# SPL by distance to adjacent habitat patch (landscape) 
# ggplot(data = metricsSG, aes(x = dist2adjPatch, y = avg_spl_low))+ theme_bw()+
#   geom_point()
# cor(metricsSG$dist2adjPatch,metricsSG$avg_spl_low)
# 
# ggplot(data = metricsSG, aes(x = dist2adjPatch, y = avg_spl_high))+ theme_bw()+
#   geom_point()
# cor(metricsSG$dist2adjPatch,metricsSG$avg_spl_high)

ggplot(data = metricsC, aes(x = dist2adjPatch, y = avg_spl_low))+ theme_bw()+
  geom_point()
cor(metricsC$dist2adjPatch,metricsC$avg_spl_low)

# ggplot(data = metricsC, aes(x = dist2adjPatch, y = avg_spl_high))+ theme_bw()+
#   geom_point()
# cor(metricsSG$dist2adjPatch,metricsSG$avg_spl_high)

ggplot(data = metricsM, aes(x = dist2adjPatch, y = avg_spl_low))+ theme_bw()+
  geom_point()
cor(metricsM$dist2adjPatch, metricsM$avg_spl_low)

ggplot(data = metricsM, aes(x = dist2adjPatch, y = avg_spl_high))+ theme_bw()+
  geom_point()
cor(metricsM$dist2adjPatch, metricsM$avg_spl_high)


# Total catch by habitat
ggplot(data = ecometrics, aes(x = habitat, y = total_abund_sum))+ theme_bw()+
  geom_boxplot()


# add label for position within seagrass bed - within, adjacent, other? 
STposition = read.csv("data/metadata/hydrophone_seagrass_position.csv")
metricsSG = left_join(metricsSG, STposition, by = "site_code")

ggplot(data = metricsSG, aes(x = position, y = avg_spl_low))+ theme_bw()+
  geom_boxplot()

SPLbySTposition = lm(avg_spl_low ~ position, data = metricsSG)
TukeyHSD(aov(SPLbySTposition))


```

## Seagrass only correlations

```{r}
metricsSG = read.csv("data/clean_data/ecometricsSeagrass.csv")
metricsSG$habitat[metricsSG$site_code == "SC"] = "seagrass"

metricsSG_num = metricsSG %>%
  select(-X, -deploy_num, -site, -bare, -Habitat, -site_code, -habitat, -soniferous, -index, -total_hab_area, -adj_hab_type)

#CorSeagrass = as.data.frame(cor(metricsSG_num, method = "pearson", use = "everything"))
#write.csv(CorSeagrass, "data/clean_data/CorrelationSeagrass.csv")

metricsSG$deploy_num = factor(metricsSG$deploy_num)

# seagrassFiltered = read.csv("data/clean_data/CorrelationSeagrass_noRedundant.csv")
# metricsSG_Filt = metricsSG_num %>%
#   select(all_of(colnames(seagrassFiltered[,-1])))


############## Low frequency ##############################

LS_halodule = ggplot(aes(x = halodule, y = avg_spl_low),data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Halodule cover")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$halodule, metricsSG$avg_spl_low, method = "pearson")

LS_zostera = ggplot(aes(x = zostera, y = avg_spl_low), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Zostera cover")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$zostera, metricsSG$avg_spl_low, method = "pearson")

LS_hab_total = ggplot(aes(x = habitat_total, y = avg_spl_low),data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Total habitat area")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$habitat_total, metricsSG$avg_spl_low, method = "pearson")

LS_saltmarsh_area = ggplot(aes(x = saltmarsh_area, y = avg_spl_low),data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Saltmarsh area")+
  ylab("Average SPL (dB re 1 uPa)")+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$saltmarsh_area, metricsSG$avg_spl_low, method = "pearson")

LS_bai_chr = ggplot(aes(x = num_bai_chr, y = avg_spl_low),data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Silver perch density")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$num_bai_chr, metricsSG$avg_spl_low, method = "pearson")

LS_planktivore = ggplot(aes(x = planktivore, y = avg_spl_low),data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Planktivore density")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$planktivore, metricsSG$avg_spl_low, method = "pearson")

LS_piscivore = ggplot(aes(x = piscivore, y = avg_spl_low),data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Piscivore density")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$piscivore, metricsSG$avg_spl_low, method = "pearson")

LS_omni_2 = ggplot(aes(x = omni_2, y = avg_spl_low),data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Omnivore density")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$omni_2, metricsSG$avg_spl_low, method = "pearson")

# temperature could actually be a seasonal pattern with chorusing
LS_temp = ggplot(aes(x = avg_temp, y = avg_spl_low),data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Water temperature")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$avg_temp, metricsSG$avg_spl_low, method = "pearson")

grid.arrange(LS_halodule, LS_zostera, LS_hab_total, LS_saltmarsh_area, LS_bai_chr,
             LS_piscivore, LS_planktivore, LS_omni_2, LS_temp, nrow = 3)

###### High frequency #############################################
HS_zostera = ggplot(aes(x = zostera, y = avg_spl_high), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Zostera cover")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$zostera, metricsSG$avg_spl_high, method = "pearson")

HS_oyster_area = ggplot(aes(x = oyster_area , y = avg_spl_high), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster area")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$oyster_area, metricsSG$avg_spl_high, method = "pearson")


HS_saltmarsh_area = ggplot(aes(x = saltmarsh_area, y = avg_spl_high), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Saltmarsh area")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$saltmarsh_area, metricsSG$avg_spl_high, method = "pearson")

HS_soniferous_S = ggplot(aes(x = soniferous_S, y = avg_spl_high), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Soniferous species richness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$soniferous_S, metricsSG$avg_spl_high, method = "pearson")

HS_comm_evenness_sum = ggplot(aes(x = comm_evenness_sum, y = avg_spl_high), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Community evenness")+
  ylab("Average SPL (dB re 1 uPa)")+
  #ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$comm_evenness_sum, metricsSG$avg_spl_high, method = "pearson")

HS_piscivore = ggplot(aes(x = piscivore, y = avg_spl_high), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Piscivore density")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$piscivore, metricsSG$avg_spl_high, method = "pearson")

HS_omni_2 = ggplot(aes(x = omni_2, y = avg_spl_high), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Omnivore density")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$omni_2, metricsSG$avg_spl_high, method = "pearson")

HS_sal_avg = ggplot(aes(x = sal_avg, y = avg_spl_high), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Salinity")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$sal_avg, metricsSG$avg_spl_high, method = "pearson")

HS_avg_temp = ggplot(aes(x = avg_temp, y = avg_spl_high), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Water temperature")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$avg_temp, metricsSG$avg_spl_high, method = "pearson")

HS_depth_m_avg = ggplot(aes(x = depth_m_avg, y = avg_spl_high), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Depth (m)")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$depth_m_avg, metricsSG$avg_spl_high, method = "pearson")

grid.arrange(HS_zostera, HS_saltmarsh_area, HS_oyster_area, HS_soniferous_S, HS_comm_evenness_sum, 
             HS_piscivore, HS_omni_2, HS_avg_temp, HS_sal_avg, HS_depth_m_avg, ncol = 4)


###### Toadfish ###################################################

T_avg_shoot_density = ggplot(aes(x = avg_shoot_density, y = ToadCallRate), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Shoot density")+
  ylab("Toadfish call rate")+
  #ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$avg_shoot_density, metricsSG$ToadCallRate, method = "pearson")

T_oyster_area  = ggplot(aes(x = oyster_area, y = ToadCallRate), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster area")+
  #ylab("Toadfish call rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$oyster_area, metricsSG$ToadCallRate, method = "pearson")

T_richness_landscape = ggplot(aes(x = richness_landscape, y = ToadCallRate), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Landscape habitat richness")+
  #ylab("Toadfish call rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$richness_landscape, metricsSG$ToadCallRate, method = "pearson")

T_comm_evenness_sum = ggplot(aes(x = comm_evenness_sum, y = ToadCallRate), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Community evenness")+
  #ylab("Toadfish call rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$comm_evenness_sum, metricsSG$ToadCallRate, method = "pearson")

T_soniferous_S = ggplot(aes(x = soniferous_S, y = ToadCallRate), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Soniferous species richness")+
  #ylab("Toadfish call rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$soniferous_S, metricsSG$ToadCallRate, method = "pearson")

T_omni_2 = ggplot(aes(x = omni_2, y = ToadCallRate), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Omnivore density")+
  #ylab("Toadfish call rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$omni_2, metricsSG$ToadCallRate, method = "pearson")

T_total_abund_sum = ggplot(aes(x = total_abund_sum, y = ToadCallRate), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Total catch density")+
  ylab("Toadfish call rate")+
  #ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$total_abund_sum, metricsSG$ToadCallRate, method = "pearson")

T_sal_avg = ggplot(aes(x = sal_avg, y = ToadCallRate), data = metricsSG)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Salinity")+
  #ylab("Toadfish call rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsSG$sal_avg, metricsSG$ToadCallRate, method = "pearson")

grid.arrange(T_avg_shoot_density, T_oyster_area, T_richness_landscape, T_soniferous_S, T_total_abund_sum,
             T_comm_evenness_sum, T_omni_2, T_sal_avg, nrow = 2)

```

## Modeling Seagrass only: 

```{r}
## Low Frequency ####
SLmetricModP = lm(avg_spl_low ~ halodule + zostera, data = metricsSG)
SLmetricModL = lm(avg_spl_low ~ habitat_total + saltmarsh_area, data = metricsSG)
SLmetricModC = lm(avg_spl_low ~ num_bai_chr + piscivore + planktivore + omni_2, data = metricsSG)
SLmetricModA = lm(avg_spl_low ~ avg_temp, data = metricsSG)
SLmetricModPL = lm(avg_spl_low ~ halodule + zostera + habitat_total + saltmarsh_area, data = metricsSG)
SLmetricModPC = lm(avg_spl_low ~ halodule + zostera + num_bai_chr + piscivore + planktivore + omni_2, data = metricsSG)
SLmetricModPA = lm(avg_spl_low ~ halodule + zostera + avg_temp, data = metricsSG)
SLmetricModLC = lm(avg_spl_low ~ habitat_total + saltmarsh_area + num_bai_chr + piscivore + planktivore + omni_2, 
                   data = metricsSG)
SLmetricModLA = lm(avg_spl_low ~ habitat_total + saltmarsh_area + avg_temp, data = metricsSG)
SLmetricModCA = lm(avg_spl_low ~ num_bai_chr + piscivore + planktivore + omni_2 + avg_temp, data = metricsSG)
SLmetricModPLC = lm(avg_spl_low ~ halodule + zostera + habitat_total + saltmarsh_area
                  + num_bai_chr + piscivore + planktivore + omni_2, data = metricsSG)
SLmetricModPLA = lm(avg_spl_low ~ halodule + zostera + habitat_total + saltmarsh_area
                  + avg_temp, data = metricsSG)
SLmetricMODPCA = lm(avg_spl_low ~ halodule + zostera + num_bai_chr + piscivore + planktivore + omni_2 + avg_temp, 
                    data = metricsSG)
SLmetricModLCA = lm(avg_spl_low ~ habitat_total + saltmarsh_area + num_bai_chr + piscivore + planktivore + omni_2 + avg_temp,
                  data = metricsSG)
SLmetricModPLCA = lm(avg_spl_low ~ halodule + zostera + habitat_total + saltmarsh_area
                  + num_bai_chr + piscivore + planktivore + omni_2 + avg_temp, data = metricsSG)

model.sel(SLmetricModPLCA, SLmetricModLCA, SLmetricMODPCA, SLmetricModPLA, SLmetricModPLC, SLmetricModCA, SLmetricModLA,
          SLmetricModLC,SLmetricModPA, SLmetricModPC, SLmetricModPL, SLmetricModP, SLmetricModL, SLmetricModC, SLmetricModA)


## High frequency ####
SHmetricModP = lm(avg_spl_high ~ zostera, data = metricsSG)
SHmetricModL = lm(avg_spl_high ~ saltmarsh_area + oyster_area, data = metricsSG)
SHmetricModC = lm(avg_spl_high ~ soniferous_S + comm_evenness_sum + piscivore + omni_2, data = metricsSG)
SHmetricModA = lm(avg_spl_high ~ avg_temp + sal_avg + depth_m_avg, data = metricsSG)
SHmetricModPL = lm(avg_spl_high ~ zostera + saltmarsh_area + oyster_area, data = metricsSG)
SHmetricModPC = lm(avg_spl_high ~ zostera + soniferous_S + comm_evenness_sum + piscivore + omni_2, data = metricsSG)
SHmetricModPA = lm(avg_spl_high ~ zostera + avg_temp + sal_avg + depth_m_avg, data = metricsSG)
SHmetricModLC = lm(avg_spl_high ~ saltmarsh_area + oyster_area + soniferous_S + comm_evenness_sum + piscivore + omni_2, 
                   data = metricsSG)
SHmetricModLA = lm(avg_spl_high ~ saltmarsh_area + oyster_area + avg_temp + sal_avg + depth_m_avg, data = metricsSG)
SHmetricModCA = lm(avg_spl_high ~ soniferous_S + comm_evenness_sum + piscivore + omni_2 + avg_temp + sal_avg + depth_m_avg,
                   data = metricsSG)
SHmetricModPLC = lm(avg_spl_high ~ zostera + saltmarsh_area + oyster_area
                  + soniferous_S + comm_evenness_sum + piscivore + omni_2, data = metricsSG)
SHmetricModPLA = lm(avg_spl_high ~ zostera + saltmarsh_area + oyster_area
                  + avg_temp + sal_avg + depth_m_avg, data = metricsSG)
SHmetricMODPCA = lm(avg_spl_high ~ zostera + soniferous_S + comm_evenness_sum + piscivore + omni_2 + avg_temp + sal_avg +
                      depth_m_avg, data = metricsSG)
SHmetricModLCA = lm(avg_spl_high ~ saltmarsh_area + oyster_area + soniferous_S + comm_evenness_sum + piscivore + omni_2 +
                      avg_temp + sal_avg + depth_m_avg, data = metricsSG)
SHmetricModPLCA = lm(avg_spl_high ~ zostera + saltmarsh_area + oyster_area + soniferous_S + comm_evenness_sum + piscivore +
                       omni_2 + avg_temp + sal_avg + depth_m_avg, data = metricsSG)

model.sel(SHmetricModPLCA, SHmetricModLCA, SHmetricMODPCA, SHmetricModPLA, SHmetricModPLC, SHmetricModCA, SHmetricModLA,
          SHmetricModLC,SHmetricModPA, SHmetricModPC, SHmetricModPL, SHmetricModP, SHmetricModL, SHmetricModC, SHmetricModA)



## Toadfish ####
STmetricModP = lm(ToadCallRate ~ avg_shoot_density, data = metricsSG)
STmetricModL = lm(ToadCallRate ~ oyster_area + richness_landscape, data = metricsSG)
STmetricModC = lm(ToadCallRate ~ soniferous_S + total_abund_sum + comm_evenness_sum + omni_2, data = metricsSG)
STmetricModA = lm(ToadCallRate ~ sal_avg, data = metricsSG)
STmetricModPL = lm(ToadCallRate ~ avg_shoot_density + oyster_area + richness_landscape,
                 data = metricsSG)
STmetricModPC = lm(ToadCallRate ~ avg_shoot_density + soniferous_S + total_abund_sum + comm_evenness_sum + omni_2, 
                   data = metricsSG)
STmetricModPA = lm(ToadCallRate ~ avg_shoot_density + sal_avg, data = metricsSG)
STmetricModLC = lm(ToadCallRate ~ oyster_area + richness_landscape + soniferous_S + total_abund_sum + comm_evenness_sum + omni_2,
                   data = metricsSG)
STmetricModLA = lm(ToadCallRate ~ oyster_area + richness_landscape + sal_avg, data = metricsSG)
STmetricModCA = lm(ToadCallRate ~ soniferous_S + total_abund_sum + comm_evenness_sum + omni_2 + sal_avg, data = metricsSG)
STmetricModPLC = lm(ToadCallRate ~ avg_shoot_density + oyster_area + richness_landscape
                  + soniferous_S + total_abund_sum + comm_evenness_sum + omni_2, data = metricsSG)
STmetricModPLA = lm(ToadCallRate ~ avg_shoot_density + oyster_area + richness_landscape
                  + sal_avg, data = metricsSG)
STmetricMODPCA = lm(ToadCallRate ~ avg_shoot_density + soniferous_S + total_abund_sum + comm_evenness_sum + omni_2 + sal_avg, 
                    data = metricsSG)
STmetricModLCA = lm(ToadCallRate ~ oyster_area + richness_landscape + soniferous_S + total_abund_sum + comm_evenness_sum + 
                    omni_2 + sal_avg, data = metricsSG)
STmetricModPLCA = lm(ToadCallRate ~ avg_shoot_density + oyster_area + richness_landscape
                     + soniferous_S + total_abund_sum + comm_evenness_sum + omni_2 + sal_avg, data = metricsSG)

model.sel(STmetricModPLCA, STmetricModLCA, STmetricMODPCA, STmetricModPLA, STmetricModPLC, STmetricModCA, STmetricModLA,
          STmetricModLC, STmetricModPA, STmetricModPC, STmetricModPL, STmetricModP, STmetricModL, STmetricModC, STmetricModA)



```

### Creek only correlations

Vast majority of ecological metrics were correlated with each other, leaving only 3 metrics

```{r}
metricsC = read.csv("data/clean_data/ecometricsCreek.csv")

# metricsC_num = metricsC %>%
#   select(-X, -deploy_num, -site, -bare, -Habitat, -site_code, -habitat, -soniferous, -index, -total_hab_area, -adj_hab_type)
# 
# CorCreek = as.data.frame(cor(metricsC_num, method = "pearson", use = "everything"))
# write.csv(CorCreek, "data/clean_data/CorrelationCreek.csv")

creekFilt = read.csv("data/clean_data/CorrelationCreek_noRedundant.csv")

##### Low frequency ####################################
CL_oyster = ggplot(aes(x = oyster, y = avg_spl_low),data = metricsC)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster cover")+
  ylab("Average SPL (dB re 1 uPa)")+
  #ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsC$oyster, metricsC$avg_spl_low, method = "pearson")

CL_sal = ggplot(aes(x = sal_avg, y = avg_spl_low),data = metricsC)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Salinity")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsC$sal_avg, metricsC$avg_spl_low, method = "pearson")

CL_dist2adj = ggplot(aes(x = dist2adjPatch, y = avg_spl_low),data = metricsC)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Isolation (Distance to adjacent habitat)")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsC$dist2adjPatch, metricsC$avg_spl_low, method = "pearson")

grid.arrange(CL_oyster, CL_dist2adj, CL_sal, nrow = 1)


##### High Frequency ########################################## 
CH_oyster = ggplot(aes(x = oyster, y = avg_spl_high),data = metricsC)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster cover")+
  ylab("Average SPL (dB re 1 uPa)")+
  #ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsC$oyster, metricsC$avg_spl_high, method = "pearson")

CH_sal = ggplot(aes(x = sal_avg, y = avg_spl_high),data = metricsC)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Salinity")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsC$sal_avg, metricsC$avg_spl_high, method = "pearson")

grid.arrange(CH_oyster, CH_sal, nrow = 1)


######### Toadfish  ###################################
CT_oyster = ggplot(aes(x = oyster, y = ToadCallRate),data = metricsC)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster Cover")+
  ylab("Toadfish Call Rate")+
  #ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsC$oyster, metricsC$ToadCallRate, method = "pearson")

CT_oyster



```

### Modeling creek

```{r}
### Low frequency ######
CL_metricModP = lm(avg_spl_low ~ oyster, data = metricsC)
CL_metricModL = lm(avg_spl_low ~ dist2adjPatch, data = metricsC)
CL_metricModA = lm(avg_spl_low ~ sal_avg, data = metricsC)
CL_metricModPL = lm(avg_spl_low ~ oyster + dist2adjPatch, data = metricsC)
CL_metricModPA = lm(avg_spl_low ~ oyster + sal_avg, data = metricsC)
CL_metricModLA = lm(avg_spl_low ~ dist2adjPatch + sal_avg, data = metricsC)
CL_metricModPLA = lm(avg_spl_low ~ oyster + dist2adjPatch + sal_avg, data = metricsC)

model.sel(CL_metricModP, CL_metricModL, CL_metricModA, CL_metricModPL, CL_metricModPA, CL_metricModLA, CL_metricModPLA)


### High frequency ######
CH_metricModP = lm(avg_spl_high ~ oyster, data = metricsC)
CH_metricModA = lm(avg_spl_high ~ sal_avg, data = metricsC)
CH_metricModPA = lm(avg_spl_high ~ oyster + sal_avg, data = metricsC)

AIC(CH_metricModP, CH_metricModA, CH_metricModPA)


```

### Mudflat only correlations

Environmental metrics were heavily correlated with landscape scale habitat metrics, tried to remove the variables with the most redundant correlation (maximize number of candidate metrics)

```{r}
metricsM = read.csv("data/clean_data/ecometricsMudflat.csv")

metricsM_num = metricsM %>%
  select(-X, -deploy_num, -site, -bare, -Habitat, -site_code, -habitat, -soniferous, -index, -total_hab_area, -adj_hab_type)

CorMud = as.data.frame(cor(metricsM_num, method = "pearson", use = "everything"))
write.csv(CorMud, "data/clean_data/CorrelationMudflat.csv")

MudflatFilt = read.csv("data/clean_data/CorrelationMudflat_noRedundant.csv")

# Low frequency & HF
MLH_seagrass_area = ggplot(aes(x = seagrass_area, y = avg_spl_low),data = metricsM)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  geom_point(aes(x = seagrass_area, y = avg_spl_high), color = "blue")+
  geom_smooth(aes(x = seagrass_area, y = avg_spl_high),method = "lm", formula = 'y~x', se=FALSE, color = "blue")+
  xlab("Seagrass cover")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsM$seagrass_area, metricsM$avg_spl_low, method = "pearson")
cor(metricsM$seagrass_area, metricsM$avg_spl_high, method = "pearson")

MLH_patchiness = ggplot(aes(x = seagrass_perim.area.ratio, y = avg_spl_low),data = metricsM)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  geom_point(aes(x = seagrass_perim.area.ratio, y = avg_spl_high), color = "blue")+
  geom_smooth(aes(x = seagrass_perim.area.ratio, y = avg_spl_high),method = "lm", formula = 'y~x', se=FALSE, color = "blue")+
  xlab("Seagrass patchiness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsM$seagrass_perim.area.ratio, metricsM$avg_spl_low, method = "pearson")
cor(metricsM$seagrass_perim.area.ratio, metricsM$avg_spl_high, method = "pearson")

MLH_saltmarsh_area = ggplot(aes(x = saltmarsh_area, y = avg_spl_low),data = metricsM)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  geom_point(aes(x = saltmarsh_area, y = avg_spl_high), color = "blue")+
  geom_smooth(aes(x = saltmarsh_area, y = avg_spl_high),method = "lm", formula = 'y~x', se=FALSE, color = "blue")+
  xlab("Saltmarsh area")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsM$saltmarsh_area, metricsM$avg_spl_low, method = "pearson")
cor(metricsM$saltmarsh_area, metricsM$avg_spl_high, method = "pearson")

MLH_richness_landscape = ggplot(aes(x = richness_landscape, y = avg_spl_low),data = metricsM)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  geom_point(aes(x = richness_landscape, y = avg_spl_high), color = "blue")+
  geom_smooth(aes(x = richness_landscape, y = avg_spl_high),method = "lm", formula = 'y~x', se=FALSE, color = "blue")+
  xlab("Landscape habitat richness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsM$richness_landscape, metricsM$avg_spl_low, method = "pearson")
cor(metricsM$richness_landscape, metricsM$avg_spl_high, method = "pearson")
  
grid.arrange(MLH_seagrass_area, MLH_patchiness, MLH_saltmarsh_area, MLH_richness_landscape, nrow = 2)


# Toadfish
MT_seagrass_area = ggplot(aes(x = seagrass_area, y = ToadCallRate),data = metricsM)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Seagrass cover")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsM$seagrass_area, metricsM$ToadCallRate, method = "pearson")

MT_patchiness = ggplot(aes(x = seagrass_perim.area.ratio, y = ToadCallRate),data = metricsM)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Seagrass patchiness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsM$seagrass_perim.area.ratio, metricsM$ToadCallRate, method = "pearson")

MT_saltmarsh_area = ggplot(aes(x = saltmarsh_area, y = ToadCallRate),data = metricsM)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Saltmarsh area")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsM$saltmarsh_area, metricsM$ToadCallRate, method = "pearson")

MT_richness_landscape = ggplot(aes(x = richness_landscape, y = ToadCallRate),data = metricsM)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Landscape habitat richness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsM$richness_landscape, metricsM$ToadCallRate, method = "pearson")

MT_comm_richness = ggplot(aes(x = comm_richness_sum, y = ToadCallRate),data = metricsM)+ theme_bw()+
  geom_point()+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Community Richness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(metricsM$comm_richness_sum, metricsM$ToadCallRate, method = "pearson")

grid.arrange(MT_seagrass_area, MT_patchiness, MT_saltmarsh_area, MT_richness_landscape, MT_comm_richness, nrow = 2)


```

