<<<<<<< HEAD
---
title: "Sound_hab_spl_correlations"
author: "Becca Van Hoeck"
date: "3/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries and data
```{r}
library(ggplot2)
library(GGally)
library(dplyr)
library(tidyr)
library(gridExtra)
library(MuMIn)

ecometrics = read.csv("data/clean_data/ecometrics.csv", header = TRUE)

# make deployment a factor to include as a random effect
ecometrics$deploy_num = factor(ecometrics$deploy_num)

```

## Updated code: Evaluate correlations among all metrics

```{r}

# Create new dataframe with only numeric metrics (remove id/character columns)
# last minute thought to include deploy_num, but it is correlated with temperature (r = 0.66), so no need
ecometrics_num = ecometrics %>%
  select(-X, -deploy_num, -site, -bare, -Habitat, -site_code, -habitat, -soniferous, -index, -total_hab_area, -adj_hab_type)

# Examine histogram of each metric - to decide on pearsons vs spearman rank correlation
# data are mostly counts, so they are poisson distributed, not normal
ecometricsLong = ecometrics_num %>%
  pivot_longer(colnames(ecometrics_num)) %>%
  as.data.frame()

# ggplot(ecometricsLong, aes(x = value))+ theme_bw()+
#   geom_histogram()+
#   facet_wrap(~name, scales = "free")

# Correlations
metricCorrEverything = cor(ecometrics_num, use = "everything", method = "pearson")

# save both methods and compare output
# write.csv(metricCorrEverything, "data/clean_data/metricCorrEverything.csv")


```

## Explore correlations within ecometrics to remove redundant variables

```{r}
# Load filtered correlations

metricCorFilt = read.csv("data/clean_data/metricCorr_everythingFiltered.csv")

ecometricsFilt = ecometrics_num %>%
  select(all_of(colnames(metricCorFilt[,-1])))

#write.csv(ecometricsFilt, "data/clean_data/ecometricsFiltered.csv")

# Retained seagrass and species densities even though they are correlated with halodule
# decided to remove algae because percent cover was so low and don't feel confident it was consistently measured - so removing to avoid reporting spurious results
```

## Correlations with sound metrics

```{r}
# soundCor = as.data.frame(metricCorFilt[c(27:30),c(2:27)])
# rownames(soundCor) = c("avg_spl_low","avg_spl_high","ToadCallRate","ToadCallRateNorm")
# 
# soundCor = as.data.frame(t(soundCor))
```

# SPL Low

```{r}
# halodule
halodule = ggplot(aes(x = halodule, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Halodule cover")+
  ylab("Average SPL (dB re 1 uPa)")+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$halodule, ecometrics$avg_spl_low, method = "pearson")

# ruppia
ruppia = ggplot(aes(x = ruppia, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Ruppia cover")+
 # ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$ruppia, ecometrics$avg_spl_low, method = "pearson")

# # Seagrass
# seagrass = ggplot(aes(x = seagrass, y = avg_spl_low),data = ecometrics)+ theme_bw()+
#   geom_point()+
#   geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
#   xlab("Seagrass cover")+
#   ylab("Average SPL (dB re 1 uPa)")+
#   theme(axis.title = element_text(size = 16), 
#         axis.text = element_text(size = 14),
#        legend.position = "none")
# cor(ecometrics$seagrass, ecometrics$avg_spl_low, method = "pearson")

# Oyster
oyster = ggplot(aes(x = oyster, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster cover")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$oyster, ecometrics$avg_spl_low, method = "pearson")

# Richness
richness = ggplot(aes(x = richness, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat richness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$richness, ecometrics$avg_spl_low, method = "pearson")

# Community Diversity
diversity = ggplot(aes(x = comm_shannonD_sum, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Community diversity")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$comm_shannonD_sum, ecometrics$avg_spl_low, method = "pearson")

# Seagrass area - landscape 
sgArea = ggplot(aes(x = seagrass_area, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Seagrass area")+
  ylab("Average SPL (dB re 1 uPa)")+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$seagrass_area, ecometrics$avg_spl_low, method = "pearson")

# Patchiness
patchiness = ggplot(aes(x = seagrass_perim.area.ratio , y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Seagrass patchiness")+
 # ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$seagrass_perim.area.ratio, ecometrics$avg_spl_low, method = "pearson")

# temp
temp = ggplot(aes(x = avg_temp, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Water temperature")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$avg_temp, ecometrics$avg_spl_low, method = "pearson")

grid.arrange(halodule, ruppia, oyster, richness, sgArea, patchiness,diversity, temp, nrow =2, ncol = 4)

```

# SPL High

```{r}

#oyster
oysterH = ggplot(aes(x = oyster, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster Cover")+
  ylab("Average SPL (dB re 1 uPa)")+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14), 
        legend.position = "none")
cor(ecometrics$oyster, ecometrics$avg_spl_high, method = "pearson")

# #algae
# algaeH = ggplot(aes(x = algae, y = avg_spl_high),data = ecometrics)+ theme_bw()+
#   geom_point(aes(color = ecometrics$habitat))+
#   geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
#   xlab("Algae Cover")+
#   ylab("Average SPL (dB re 1 uPa)")+
#   theme(axis.title = element_text(size = 16), 
#         axis.text = element_text(size = 16))
# cor(ecometrics$algae, ecometrics$avg_spl_high, method = "pearson")

#richness
richnessH = ggplot(aes(x = richness, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat Richness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$richness, ecometrics$avg_spl_high, method = "pearson")

#habitat total
totalHabH = ggplot(aes(x = habitat_total, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat total")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14), 
        legend.position = "none")
cor(ecometrics$habitat_total, ecometrics$avg_spl_high, method = "pearson")

#avg_temp
tempH = ggplot(aes(x = avg_temp, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Water Temperature")+
  ylab("Average SPL (dB re 1 uPa)")+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14), 
        legend.position = "none")
cor(ecometrics$avg_temp, ecometrics$avg_spl_high, method = "pearson")

#salinity
salinityH = ggplot(aes(x = sal_avg, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Salinity")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14), 
        legend.position = "none")
cor(ecometrics$sal_avg, ecometrics$avg_spl_high, method = "pearson")

#depth
depthH = ggplot(aes(x = depth_m_avg, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Depth")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14), 
        legend.position = "none")
cor(ecometrics$depth_m_avg, ecometrics$avg_spl_high, method = "pearson")



grid.arrange(oysterH, richnessH, totalHabH,tempH, salinityH, depthH, nrow = 2,ncol = 3)

```

# Toadfish

```{r}

# Oyster
oysterT = ggplot(aes(x = oyster, y = ToadCallRate),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster Cover")+
  ylab("Toadfish Call Rate")+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$oyster, ecometrics$ToadCallRate, method = "pearson")

# #algae
# algaeT = ggplot(aes(x = algae, y = ToadCallRate),data = ecometrics)+ theme_bw()+
#   geom_point(aes(color = habitat))+
#   geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
#   xlab("Algae Cover")+
#   ylab("Toadfish Call Rate")+
#   theme(axis.title = element_text(size = 16), 
#         axis.text = element_text(size = 16))
# cor(ecometrics$algae, ecometrics$ToadCallRate, method = "pearson")

#richness comb
richnessT = ggplot(aes(x = richness_comb, y = ToadCallRate),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat Richness")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$richness_comb, ecometrics$ToadCallRate, method = "pearson")

#habitat total
totalHabT = ggplot(aes(x = habitat_total, y = ToadCallRate),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat total")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$habitat_total, ecometrics$ToadCallRate, method = "pearson")

grid.arrange(oysterT,richnessT,totalHabT, ncol = 3)

## Summary of toadfish call rates
toadfish_rates = ecometrics %>%
  select(site, habitat,deploy_num,ToadCallRate, ToadCallRateNorm) %>%
  filter(ToadCallRate > 0)

min(toadfish_rates$ToadCallRate)
max(toadfish_rates$ToadCallRate)
unique(toadfish_rates$habitat)
unique(toadfish_rates$deploy_num)


```

## First attempt at modeling SPL (Low) and ecometrics

```{r}

# This currently doesn't account for habitat type - which likely confounds some trends

metricModP = lm(avg_spl_low ~ halodule + ruppia + oyster + richness, data = ecometrics)
metricModL = lm(avg_spl_low ~ seagrass_area + seagrass_perim.area.ratio, data = ecometrics)
metricModC = lm(avg_spl_low ~ comm_shannonD_sum, data = ecometrics)
metricModA = lm(avg_spl_low ~ avg_temp, data = ecometrics)
metricModPL = lm(avg_spl_low ~ halodule + ruppia + oyster + richness + seagrass_area + seagrass_perim.area.ratio,
                 data = ecometrics)
metricModPC = lm(avg_spl_low ~ halodule + ruppia + oyster + richness + comm_shannonD_sum, data = ecometrics)
metricModPA = lm(avg_spl_low ~ halodule + ruppia + oyster + richness + avg_temp, data = ecometrics)
metricModLC = lm(avg_spl_low ~ seagrass_area + seagrass_perim.area.ratio + comm_shannonD_sum, data = ecometrics)
metricModLA = lm(avg_spl_low ~ seagrass_area + seagrass_perim.area.ratio + avg_temp, data = ecometrics)
metricModCA = lm(avg_spl_low ~ comm_shannonD_sum + avg_temp, data = ecometrics)
metricModPLC = lm(avg_spl_low ~ halodule + ruppia + oyster + richness + seagrass_area + seagrass_perim.area.ratio
                  + comm_shannonD_sum, data = ecometrics)
metricModPLA = lm(avg_spl_low ~ halodule + ruppia + oyster + richness + seagrass_area + seagrass_perim.area.ratio
                  + avg_temp, data = ecometrics)
metricMODPCA = lm(avg_spl_low ~ halodule + ruppia + oyster + richness + comm_shannonD_sum + avg_temp, data = ecometrics)
metricModLCA = lm(avg_spl_low ~ seagrass_area + seagrass_perim.area.ratio + comm_shannonD_sum + avg_temp,
                  data = ecometrics)
metricModPLCA = lm(avg_spl_low ~ halodule + ruppia + oyster + richness + seagrass_area + seagrass_perim.area.ratio
                  + comm_shannonD_sum + avg_temp, data = ecometrics)

AIC(metricModPLCA, metricModLCA, metricMODPCA, metricModPLA, metricModPLC, metricModCA, metricModLA, metricModLC,
    metricModPA, metricModPC, metricModPL, metricModP, metricModL, metricModC, metricModA) 

model.sel(metricModPLCA, metricModLCA, metricMODPCA, metricModPLA, metricModPLC, metricModCA, metricModLA, metricModLC,
    metricModPA, metricModPC, metricModPL, metricModP, metricModL, metricModC, metricModA)

# P, PA, CA, & C are all indiscernible by AICc
# AICc is a correction for small sample size - should likely use here. 

```

## Modeling high frequency SPL and candidate ecometrics

```{r}
# edit to High vars and change names
HmetricModP = lm(avg_spl_high ~ oyster + richness, data = ecometrics)
HmetricModL = lm(avg_spl_high ~ habitat_total, data = ecometrics)
HmetricModA = lm(avg_spl_high ~ avg_temp + sal_avg + depth_m_avg, data = ecometrics)
HmetricModPL = lm(avg_spl_high ~ oyster + richness + habitat_total, data = ecometrics)
HmetricModPA = lm(avg_spl_high ~ oyster + richness + avg_temp + sal_avg + depth_m_avg, data = ecometrics)
HmetricModLA = lm(avg_spl_high ~ habitat_total + avg_temp + sal_avg + depth_m_avg, data = ecometrics)
HmetricModPLA = lm(avg_spl_high ~ oyster + richness + habitat_total
                  + avg_temp + sal_avg + depth_m_avg, data = ecometrics)

AIC(HmetricModPLA, HmetricModLA, HmetricModPA, HmetricModPL, HmetricModP, HmetricModL, HmetricModA) 

model.sel(HmetricModPLA, HmetricModLA, HmetricModPA, HmetricModPL, HmetricModP, HmetricModL, HmetricModA)


```

### Modeling toadfish

```{r}

TmetricModP = lm(ToadCallRate ~ oyster + richness, data = ecometrics)
TmetricModL = lm(ToadCallRate ~ habitat_total, data = ecometrics)
TmetricModPL = lm(ToadCallRate ~ oyster + richness + habitat_total,
                 data = ecometrics)


AIC(TmetricModPL, TmetricModP, TmetricModL) 

model.sel(TmetricModPL, TmetricModP, TmetricModL)



```














#### END HERER FOR NOW!

## Build model to explore variation in SPL

1. Using predictor variables that crossed a 0.3 correlation threshold, examine simple linear model with all candidate predictors
2. Evaluate model fit and evidence to retain or drop each predictor until a final model is reached

** Need to consider whether a mixed-effects model structure is more appropriate - random effect of deployment, site? should habitat type be a fixed or random effect?, should any interactions be included?**

Questions: 
1. Do I need to standardize or transform predictors?
2. How to evaluate if lm is sufficient, or should include mixed effects?
3. How to incorporate the variable effects of habitat? Can I exclude mudflats?

```{r}
#library(nlme)

# HIGH FREQUENCY - 
#didn't include avg_blade_length even though strong correlation Possibly explore seagrass alone

highMod1 = lm(avg_spl_high ~ totalcover + oyster + evenness + depth_m_avg + 
                temp_avg + sal_avg + comm_evenness_sum + piscivore + habitat, data = ecometrics)


#re-level habitat to mudflat as base case: 
spl ~ creek + creek_cover + seagrass + seagrasscover

# recommendation: 
# build ecologicaly reasonable models 
# possibility incorporate "biotic effects", "env effects" or not... 
# then compare or average the models

## this doesn't work due to different sizes - missing data
#ecometrics$highmodpredict = predict(highMod2)

# Selected highMod2 due to lowest ACI, but the conf intervals for many of the effects overlap with zero
# doesn't this suggest no effect of those variables?
confint(highMod2)

# inspect residuals
residplot <- function(model){
  ggplot(model,aes(x=.fitted,y=.resid))+ 
    geom_point()+
    labs(x="Fitted values",y="Residuals")
  }
# inspect quantiles 
qqplot <- function(model){
  q1 <- ggplot(model,aes(sample=.stdresid))
  q1+geom_point(stat="qq")+geom_abline(slope=1,intercept=0)+
    labs(x="Theoretical Quantiles",y="Standardized residuals")
}

residplot(highMod2)
qqplot(highMod2)
confint(highMod2)

# LOW FREQUENCY 
#should I include interaction between habitat and total cover?

lowMod1 = lm(avg_spl_low ~ oyster + depth_m_avg + total_abund_sum + comm_richness_sum +
                 comm_evenness_sum + habitat, data = ecometrics)
summary(lowMod1)
drop1(lowMod1)

lowMod2 = lm(avg_spl_low ~ oyster + depth_m_avg + 
                 comm_evenness_sum, data = ecometrics)
summary(lowMod2)
drop1(lowMod2)

AIC(lowMod1, lowMod2)

# Selected lowMod2 for trial, but really not distinguishable by AIC
confint(lowMod2)

residplot(lowMod2)
qqplot(lowMod2)

```

## Variation within habitat type

```{r}
# Seagrass
sgMetrics = ecometrics %>%
  filter(habitat == "seagrass")

sound_seagrass = sgMetrics %>%
  select(site, habitat, totalcover, seagrass_comb, oyster, saltmarsh, richness, evenness,
         avg_shoot_density, avg_blade_length,
        avg_spl_low, avg_spl_high, BI_low, BI_high)

ggpairs(sound_seagrass[,3:14])

# # Creek
# creekMetrics = ecometrics %>%
#   filter(habitat == "creek")
# 
# sound_creek = creekMetrics %>%
#   select(site, habitat, totalcover, seagrass_comb, oyster, saltmarsh, richness, evenness,
#          avg_shoot_density, avg_blade_length,
#         avg_spl_low, avg_spl_high, BI_low, BI_high)
# 
# ggpairs(sound_creek,3:14)



```

## Plots exploring pairwise correlation and variation among habitat types

```{r}

# add habitat label and filter to only seagrass

#Benthic metrics
ggplot(aes(x = richness, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = richness_comb, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = evenness , y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = totalcover, y = avg_spl_low, color = habitat), data = ecometrics)+ theme_bw()+
  geom_point(size = 3)+
  geom_smooth(method = "lm", se = FALSE)+
  scale_color_discrete(name = "Habitat type")+
  ylab("Average sound pressure level (db re 1 uPa")+ 
  xlab("Average percent cover")+
  theme(axis.text = element_text(size = 16), 
        axis.title = element_text(size = 18), 
        legend.title = element_text(size = 18), 
        legend.text = element_text(size = 16))

#Habitat Metrics
ggplot(aes(x = seagrass_comb, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = saltmarsh, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = saltmarsh, y = avg_spl_high, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = oyster, y = avg_spl_high, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = oyster, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

# Community metrics
ggplot(aes(x = total_abund_sum, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = comm_evenness_sum, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = comm_richness_sum, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = X1_Depth_m, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()


```