<<<<<<< HEAD
---
title: "Sound_hab_spl_correlations"
author: "Becca Van Hoeck"
date: "3/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries and data
```{r}
library(ggplot2)
library(GGally)
library(dplyr)
library(tidyr)
library(gridExtra)
library(MuMIn)

ecometrics = read.csv("data/clean_data/ecometrics.csv", header = TRUE)

```

## Updated code: Evaluate correlations among all metrics

```{r}

# Create new dataframe with only numeric metrics (remove id/character columns)
# last minute thought to include deploy_num, but it is correlated with temperature (r = 0.66), so no need
ecometrics$deploy_num = as.numeric(ecometrics$deploy_num)
ecometrics_num = ecometrics %>%
  select(-X, -site, -bare, -Habitat, -site_code, -site_code2, -habitat, -soniferous, -index, -total_hab_area, -adj_hab_type)


# Examine histogram of each metric - to decide on pearsons vs spearman rank correlation
# data are mostly counts, so they are poisson distributed, not normal
# ecometricsLong = ecometrics_num %>%
#   pivot_longer(colnames(ecometrics_num)) %>%
#   as.data.frame()

# ggplot(ecometricsLong, aes(x = value))+ theme_bw()+
#   geom_histogram()+
#   facet_wrap(~name, scales = "free")

# Correlations
metricCorrEverything = cor(ecometrics_num, use = "everything", method = "pearson")
write.csv(metricCorrEverything, "data/clean_data/metricCorrEverything.csv")


```

## Explore correlations within ecometrics to remove redundant variables

```{r}
# Load filtered correlations

metricCorFilt = read.csv("data/clean_data/metricCorr_everythingFiltered.csv")

ecometricsFilt = ecometrics_num %>%
  select(all_of(colnames(metricCorFilt[,-1])))

#write.csv(ecometricsFilt, "data/clean_data/ecometricsFiltered.csv")

# Retained seagrass and species densities even though they are correlated with halodule
# decided to remove algae because percent cover was so low and don't feel confident it was consistently measured - so removing to avoid reporting spurious results
```

# SPL Low

```{r}

# halodule
halodule = ggplot(aes(x = halodule, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Halodule cover")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$halodule, ecometrics$avg_spl_low, method = "pearson")

# ruppia
ruppia = ggplot(aes(x = ruppia, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Ruppia cover")+
 # ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$ruppia, ecometrics$avg_spl_low, method = "pearson")

# Richness
richness = ggplot(aes(x = richness, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat richness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$richness, ecometrics$avg_spl_low, method = "pearson")

# Seagrass core area - landscape 
sgCoreArea = ggplot(aes(x = seagrass_core.area, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Seagrass core area")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$seagrass_core.area, ecometrics$avg_spl_low, method = "pearson")

# Seagrass Patchiness
patchiness = ggplot(aes(x = seagrass_perim.area.ratio , y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Seagrass patchiness")+
 # ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$seagrass_perim.area.ratio, ecometrics$avg_spl_low, method = "pearson")

# Oyster perimeter
oysterPerim = ggplot(aes(x = oyster_perimeter , y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster perimeter")+
 # ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$oyster_perimeter, ecometrics$avg_spl_low, method = "pearson")

# Community Diversity
diversity = ggplot(aes(x = comm_shannonD_sum, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Community diversity")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$comm_shannonD_sum, ecometrics$avg_spl_low, method = "pearson")

# Silver perch cpue
perch = ggplot(aes(x = num_bai_chr, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Silver perch CPUE")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$num_bai_chr, ecometrics$avg_spl_low, method = "pearson")

# temp
temp = ggplot(aes(x = avg_temp, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Water temperature")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$avg_temp, ecometrics$avg_spl_low, method = "pearson")


grid.arrange(halodule, ruppia, richness, sgCoreArea, patchiness, oysterPerim, diversity, perch, temp, nrow =3)

```

# SPL High

```{r}
cor_spl_high = read.csv("data/clean_data/metricCorrEverything_highSPL.csv")


# Shannon diversity
diversityH = ggplot(aes(x = shannonD, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat Diversity")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$shannonD, ecometrics$avg_spl_high, method = "pearson")

#richness_comb
richnessH = ggplot(aes(x = richness_comb, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat Richness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$richness_comb, ecometrics$avg_spl_high, method = "pearson")

# total cover
totalCoverH = ggplot(aes(x = total_cover, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Total habitat cover")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$total_cover, ecometrics$avg_spl_high, method = "pearson")

# Oyster perimeter
oysterPerimH = ggplot(aes(x = oyster_perimeter, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster perimeter - Landscape")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$oyster_perimeter, ecometrics$avg_spl_high, method = "pearson")

# Soniferous species richness
soniferousSH = ggplot(aes(x = soniferous_S, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Soniferous species richness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$soniferous_S, ecometrics$avg_spl_high, method = "pearson")

# deploy_num
deployH = ggplot(aes(x = deploy_num, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Deployment")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$deploy_num, ecometrics$avg_spl_high, method = "pearson")

#avg_temp
tempH = ggplot(aes(x = avg_temp, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Water Temperature")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14), 
        legend.position = "none")
cor(ecometrics$avg_temp, ecometrics$avg_spl_high, method = "pearson")

#salinity
salinityH = ggplot(aes(x = sal_avg, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Salinity")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14), 
        legend.position = "none")
cor(ecometrics$sal_avg, ecometrics$avg_spl_high, method = "pearson")

#depth
depthH = ggplot(aes(x = depth_m_avg, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Depth")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14), 
        legend.position = "none")
cor(ecometrics$depth_m_avg, ecometrics$avg_spl_high, method = "pearson")


#grid.arrange(oysterH, richnessH, totalHabH,tempH, salinityH, depthH, nrow = 2,ncol = 3)
grid.arrange(diversityH, richnessH, totalCoverH, oysterPerimH, soniferousSH, deployH,tempH, salinityH, depthH, nrow = 3)

```

# Toadfish

```{r}


# deploy_num
# richness_comb
# total_cover
# carnivore
# seagrass_perimeter
# oyster_core.area
# habitat_total


#richness comb
richnessT = ggplot(aes(x = richness_comb, y = ToadCallRate),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat Richness")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$richness_comb, ecometrics$ToadCallRate, method = "pearson")

# total cover
totalCoverT = ggplot(aes(x = total_cover, y = ToadCallRate),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Total habitat cover")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$total_cover, ecometrics$ToadCallRate, method = "pearson")

#oyster area
oysterAreaT = ggplot(aes(x = oyster_area, y = ToadCallRate),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster area")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$oyster_area, ecometrics$ToadCallRate, method = "pearson")

# deploy_num
deployT = ggplot(aes(x = deploy_num, y = ToadCallRate),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Deployment")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$deploy_num, ecometrics$ToadCallRate, method = "pearson")


grid.arrange(richnessT, totalCoverT, oysterAreaT, deployT, ncol = 2)

## Summary of toadfish call rates
toadfish_rates = ecometrics %>%
  select(site, habitat,deploy_num,ToadCallRate, ToadCallRateNorm) %>%
  filter(ToadCallRate > 0)

min(toadfish_rates$ToadCallRate)
max(toadfish_rates$ToadCallRate)
unique(toadfish_rates$habitat)
unique(toadfish_rates$deploy_num)


```

# Silver Perch

```{r}

# richness
# shannonD
# seagrass
# richness_comb
# comm_shannonD_sum
# seagrass_core_area
# dist2adjPatch
# avgTempNight


```

## First attempt at modeling SPL (Low) and ecometrics

```{r}

# This currently doesn't account for habitat type - which likely confounds some trends
metricModP = lm(avg_spl_low ~ halodule + ruppia + richness, data = ecometrics)
metricModL = lm(avg_spl_low ~ seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter, data = ecometrics)
metricModC = lm(avg_spl_low ~ comm_shannonD_sum + num_bai_chr, data = ecometrics)
metricModA = lm(avg_spl_low ~ avg_temp, data = ecometrics)
metricModPL = lm(avg_spl_low ~ halodule + ruppia + richness +  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter,
                 data = ecometrics)
metricModPC = lm(avg_spl_low ~ halodule + ruppia + richness + comm_shannonD_sum + num_bai_chr, data = ecometrics)
metricModPA = lm(avg_spl_low ~ halodule + ruppia + richness + avg_temp, data = ecometrics)
metricModLC = lm(avg_spl_low ~  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter + comm_shannonD_sum + num_bai_chr, data = ecometrics)
metricModLA = lm(avg_spl_low ~  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter + avg_temp, data = ecometrics)
metricModCA = lm(avg_spl_low ~ comm_shannonD_sum + num_bai_chr + avg_temp, data = ecometrics)
metricModPLC = lm(avg_spl_low ~ halodule + ruppia + richness +  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter
                  + comm_shannonD_sum + num_bai_chr, data = ecometrics)
metricModPLA = lm(avg_spl_low ~ halodule + ruppia + richness +  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter
                  + avg_temp, data = ecometrics)
metricMODPCA = lm(avg_spl_low ~ halodule + ruppia + richness + comm_shannonD_sum + num_bai_chr + avg_temp, data = ecometrics)
metricModLCA = lm(avg_spl_low ~  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter + comm_shannonD_sum + num_bai_chr + avg_temp,
                  data = ecometrics)
metricModPLCA = lm(avg_spl_low ~ halodule + ruppia + richness +  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter
                  + comm_shannonD_sum + num_bai_chr + avg_temp, data = ecometrics)

AIC(metricModPLCA, metricModLCA, metricMODPCA, metricModPLA, metricModPLC, metricModCA, metricModLA, metricModLC,
    metricModPA, metricModPC, metricModPL, metricModP, metricModL, metricModC, metricModA) 

model.sel(metricModPLCA, metricModLCA, metricMODPCA, metricModPLA, metricModPLC, metricModCA, metricModLA, metricModLC,
    metricModPA, metricModPC, metricModPL, metricModP, metricModL, metricModC, metricModA)

# PLA, PL, C, LA, CA are all indiscernible by AICc
# AICc is a correction for small sample size - should likely use here. 

# AIC identified PLA as the best fit

```

## Modeling high frequency SPL and candidate ecometrics

```{r}
HmetricModP = lm(avg_spl_low ~ shannonD + richness_comb + total_cover , data = ecometrics)
HmetricModL = lm(avg_spl_low ~ oyster_perimeter, data = ecometrics)
HmetricModC = lm(avg_spl_low ~ soniferous_S, data = ecometrics)
HmetricModA = lm(avg_spl_low ~ deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)
HmetricModPL = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + oyster_perimeter, data = ecometrics)
HmetricModPC = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + soniferous_S, data = ecometrics)
HmetricModPA = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)
HmetricModLC = lm(avg_spl_low ~ oyster_perimeter + soniferous_S, data = ecometrics)
HmetricModLA = lm(avg_spl_low ~ oyster_perimeter + deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)
HmetricModCA = lm(avg_spl_low ~ soniferous_S + deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)
HmetricModPLC = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + oyster_perimeter + soniferous_S, data = ecometrics)
HmetricModPLA = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + oyster_perimeter
                  + deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)
HmetricModPCA = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + soniferous_S + deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)
HmetricModLCA = lm(avg_spl_low ~ oyster_perimeter + soniferous_S + deploy_num + avg_temp + depth_m_avg + sal_avg,
                  data = ecometrics)
HmetricModPLCA = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + oyster_perimeter
                  + soniferous_S + deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)

model.sel(HmetricModPLCA, HmetricModLCA, HmetricModPCA, HmetricModPLA, HmetricModPLC, HmetricModCA, HmetricModLA, HmetricModLC,
    HmetricModPA, HmetricModPC, HmetricModPL, HmetricModP, HmetricModL, HmetricModC, HmetricModA)

AIC(HmetricModPLCA, HmetricModLCA, HmetricModPCA, HmetricModPLA, HmetricModPLC, HmetricModCA, HmetricModLA, HmetricModLC,
    HmetricModPA, HmetricModPC, HmetricModPL, HmetricModP, HmetricModL, HmetricModC, HmetricModA)

# within 2 AIC
# AICc: PL & PLC
# AIC: PLC, PLCA, PLA, & PL 

# Variance partitioning High Frequency:
# the math is correct there are negative shared variances - look into more to understand
H_patch = summary(HmetricModPLC)$r.squared - summary(HmetricModLC)$r.squared
H_landscape = summary(HmetricModPLC)$r.squared - summary(HmetricModPC)$r.squared
H_comm = summary(HmetricModPLC)$r.squared - summary(HmetricModPL)$r.squared

H_unexplained = 1- summary(HmetricModPLC)$r.squared

# sum of unique explanation is greater than the total?? something seems wrong there
# is the unique explanation 37% of the total (or 37% of the 70% explained?)
Htotal_explained = summary(HmetricModPLC)$r.squared
H_patch + H_landscape + H_comm


# advises against variance partitioning with more than three categories - can you variable weights from AIC to justify which metric categories should be included. 
```

### Modeling toadfish

```{r}

TmetricModP = lm(ToadCallRate ~ richness_comb + total_cover, data = ecometrics)
TmetricModL = lm(ToadCallRate ~ oyster_area, data = ecometrics)
TmetricModA = lm(ToadCallRate ~ deploy_num, data = ecometrics)
TmetricModPL = lm(ToadCallRate ~ richness_comb + total_cover + oyster_area, data = ecometrics)
TmetricModPA = lm(ToadCallRate ~ richness_comb + total_cover, data = ecometrics)
TmetricModLA = lm(ToadCallRate ~ oyster_area + deploy_num, data = ecometrics)
TmetricModPLA = lm(ToadCallRate ~ richness_comb + total_cover + oyster_area + deploy_num, data = ecometrics)

AIC(TmetricModPLA, TmetricModPL, TmetricModPA, TmetricsModLA, TmetricModP, TmetricModL, TmetricModA) 

model.sel(TmetricModPLA, TmetricModPL, TmetricModPA, TmetricsModLA, TmetricModP, TmetricModL, TmetricModA)

#AIC: PLA
#AICc: PLA

# attempting variance partitioning 

Tpatch = summary(TmetricModPLA)$r.squared - summary(TmetricModLA)$r.squared
Tlandscape = summary(TmetricModPLA)$r.squared - summary(TmetricModPA)$r.squared
Tabiotic = summary(TmetricModPLA)$r.squared - summary(TmetricModPL)$r.squared
Tunexplained = 1 - summary(TmetricModPLA)$r.squared


```














#### END HERER FOR NOW!

## Build model to explore variation in SPL

1. Using predictor variables that crossed a 0.3 correlation threshold, examine simple linear model with all candidate predictors
2. Evaluate model fit and evidence to retain or drop each predictor until a final model is reached

** Need to consider whether a mixed-effects model structure is more appropriate - random effect of deployment, site? should habitat type be a fixed or random effect?, should any interactions be included?**

Questions: 
1. Do I need to standardize or transform predictors?
2. How to evaluate if lm is sufficient, or should include mixed effects?
3. How to incorporate the variable effects of habitat? Can I exclude mudflats?

```{r}
#library(nlme)

# HIGH FREQUENCY - 
#didn't include avg_blade_length even though strong correlation Possibly explore seagrass alone

highMod1 = lm(avg_spl_high ~ totalcover + oyster + evenness + depth_m_avg + 
                temp_avg + sal_avg + comm_evenness_sum + piscivore + habitat, data = ecometrics)


#re-level habitat to mudflat as base case: 
spl ~ creek + creek_cover + seagrass + seagrasscover

# recommendation: 
# build ecologicaly reasonable models 
# possibility incorporate "biotic effects", "env effects" or not... 
# then compare or average the models

## this doesn't work due to different sizes - missing data
#ecometrics$highmodpredict = predict(highMod2)

# Selected highMod2 due to lowest ACI, but the conf intervals for many of the effects overlap with zero
# doesn't this suggest no effect of those variables?
confint(highMod2)

# inspect residuals
residplot <- function(model){
  ggplot(model,aes(x=.fitted,y=.resid))+ 
    geom_point()+
    labs(x="Fitted values",y="Residuals")
  }
# inspect quantiles 
qqplot <- function(model){
  q1 <- ggplot(model,aes(sample=.stdresid))
  q1+geom_point(stat="qq")+geom_abline(slope=1,intercept=0)+
    labs(x="Theoretical Quantiles",y="Standardized residuals")
}

residplot(highMod2)
qqplot(highMod2)
confint(highMod2)

# LOW FREQUENCY 
#should I include interaction between habitat and total cover?

lowMod1 = lm(avg_spl_low ~ oyster + depth_m_avg + total_abund_sum + comm_richness_sum +
                 comm_evenness_sum + habitat, data = ecometrics)
summary(lowMod1)
drop1(lowMod1)

lowMod2 = lm(avg_spl_low ~ oyster + depth_m_avg + 
                 comm_evenness_sum, data = ecometrics)
summary(lowMod2)
drop1(lowMod2)

AIC(lowMod1, lowMod2)

# Selected lowMod2 for trial, but really not distinguishable by AIC
confint(lowMod2)

residplot(lowMod2)
qqplot(lowMod2)

```

## Variation within habitat type

```{r}
# Seagrass
sgMetrics = ecometrics %>%
  filter(habitat == "seagrass")

sound_seagrass = sgMetrics %>%
  select(site, habitat, totalcover, seagrass_comb, oyster, saltmarsh, richness, evenness,
         avg_shoot_density, avg_blade_length,
        avg_spl_low, avg_spl_high, BI_low, BI_high)

ggpairs(sound_seagrass[,3:14])

# # Creek
# creekMetrics = ecometrics %>%
#   filter(habitat == "creek")
# 
# sound_creek = creekMetrics %>%
#   select(site, habitat, totalcover, seagrass_comb, oyster, saltmarsh, richness, evenness,
#          avg_shoot_density, avg_blade_length,
#         avg_spl_low, avg_spl_high, BI_low, BI_high)
# 
# ggpairs(sound_creek,3:14)



```

## Plots exploring pairwise correlation and variation among habitat types

```{r}

# add habitat label and filter to only seagrass

#Benthic metrics
ggplot(aes(x = richness, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = richness_comb, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = evenness , y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = totalcover, y = avg_spl_low, color = habitat), data = ecometrics)+ theme_bw()+
  geom_point(size = 3)+
  geom_smooth(method = "lm", se = FALSE)+
  scale_color_discrete(name = "Habitat type")+
  ylab("Average sound pressure level (db re 1 uPa")+ 
  xlab("Average percent cover")+
  theme(axis.text = element_text(size = 16), 
        axis.title = element_text(size = 18), 
        legend.title = element_text(size = 18), 
        legend.text = element_text(size = 16))

#Habitat Metrics
ggplot(aes(x = seagrass_comb, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = saltmarsh, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = saltmarsh, y = avg_spl_high, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = oyster, y = avg_spl_high, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = oyster, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

# Community metrics
ggplot(aes(x = total_abund_sum, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = comm_evenness_sum, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = comm_richness_sum, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()

ggplot(aes(x = X1_Depth_m, y = avg_spl_low, color = habitat), data = ecometrics)+
  geom_point()


```