<<<<<<< HEAD
---
title: "Sound_hab_spl_correlations"
author: "Becca Van Hoeck"
date: "3/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries and data
```{r}
library(ggplot2)
library(GGally)
library(dplyr)
library(tidyr)
library(gridExtra)
library(MuMIn)

ecometrics = read.csv("data/clean_data/ecometrics.csv", header = TRUE)

```

## Updated code: Evaluate correlations among all metrics

```{r}

# Create new dataframe with only numeric metrics (remove id/character columns)
# last minute thought to include deploy_num, but it is correlated with temperature (r = 0.66), so no need
ecometrics$deploy_num = as.numeric(ecometrics$deploy_num)
ecometrics_num = ecometrics %>%
  select(-X, -site, -bare, -Habitat, -site_code, -site_code2, -habitat, -soniferous, -index, -total_hab_area, -adj_hab_type)


# Examine histogram of each metric - to decide on pearsons vs spearman rank correlation
# data are mostly counts, so they are poisson distributed, not normal
# ecometricsLong = ecometrics_num %>%
#   pivot_longer(colnames(ecometrics_num)) %>%
#   as.data.frame()

# ggplot(ecometricsLong, aes(x = value))+ theme_bw()+
#   geom_histogram()+
#   facet_wrap(~name, scales = "free")

# Correlations
metricCorrEverything = cor(ecometrics_num, use = "everything", method = "pearson")
write.csv(metricCorrEverything, "data/clean_data/metricCorrEverything.csv")


```

## Explore correlations within ecometrics to remove redundant variables

```{r}
# Load filtered correlations

metricCorFilt = read.csv("data/clean_data/metricCorr_everythingFiltered.csv")

ecometricsFilt = ecometrics_num %>%
  select(all_of(colnames(metricCorFilt[,-1])))

#write.csv(ecometricsFilt, "data/clean_data/ecometricsFiltered.csv")

# Retained seagrass and species densities even though they are correlated with halodule
# decided to remove algae because percent cover was so low and don't feel confident it was consistently measured - so removing to avoid reporting spurious results
```

# SPL Low

```{r}

# halodule
halodule = ggplot(aes(x = halodule, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Halodule cover")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$halodule, ecometrics$avg_spl_low, method = "pearson")

# ruppia
ruppia = ggplot(aes(x = ruppia, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Ruppia cover")+
 # ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$ruppia, ecometrics$avg_spl_low, method = "pearson")

# Richness
richness = ggplot(aes(x = richness, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat richness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$richness, ecometrics$avg_spl_low, method = "pearson")

# Seagrass core area - landscape 
sgCoreArea = ggplot(aes(x = seagrass_core.area, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Seagrass core area")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$seagrass_core.area, ecometrics$avg_spl_low, method = "pearson")

# Seagrass Patchiness
patchiness = ggplot(aes(x = seagrass_perim.area.ratio , y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Seagrass patchiness")+
 # ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$seagrass_perim.area.ratio, ecometrics$avg_spl_low, method = "pearson")

# Oyster perimeter
oysterPerim = ggplot(aes(x = oyster_perimeter , y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster perimeter")+
 # ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$oyster_perimeter, ecometrics$avg_spl_low, method = "pearson")

# Community Diversity
diversity = ggplot(aes(x = comm_shannonD_sum, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Community diversity")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$comm_shannonD_sum, ecometrics$avg_spl_low, method = "pearson")

# Silver perch cpue
perch = ggplot(aes(x = num_bai_chr, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Silver perch CPUE")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$num_bai_chr, ecometrics$avg_spl_low, method = "pearson")

# temp
temp = ggplot(aes(x = avg_temp, y = avg_spl_low),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Water temperature")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$avg_temp, ecometrics$avg_spl_low, method = "pearson")


grid.arrange(halodule, ruppia, richness, sgCoreArea, patchiness, oysterPerim, diversity, perch, temp, nrow =3)

```

# SPL High

```{r}
#cor_spl_high = read.csv("data/clean_data/metricCorrEverything_highSPL.csv")


# Shannon diversity
diversityH = ggplot(aes(x = shannonD, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat Diversity")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$shannonD, ecometrics$avg_spl_high, method = "pearson")

#richness_comb
richnessH = ggplot(aes(x = richness_comb, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat Richness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$richness_comb, ecometrics$avg_spl_high, method = "pearson")

# total cover
totalCoverH = ggplot(aes(x = total_cover, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Total habitat cover")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$total_cover, ecometrics$avg_spl_high, method = "pearson")

# Oyster perimeter
oysterPerimH = ggplot(aes(x = oyster_perimeter, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster perimeter - Landscape")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$oyster_perimeter, ecometrics$avg_spl_high, method = "pearson")

# Soniferous species richness
soniferousSH = ggplot(aes(x = soniferous_S, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Soniferous species richness")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$soniferous_S, ecometrics$avg_spl_high, method = "pearson")

# deploy_num
deployH = ggplot(aes(x = deploy_num, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Deployment")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14),
        legend.position = "none")
cor(ecometrics$deploy_num, ecometrics$avg_spl_high, method = "pearson")

#avg_temp
tempH = ggplot(aes(x = avg_temp, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Water Temperature")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14), 
        legend.position = "none")
cor(ecometrics$avg_temp, ecometrics$avg_spl_high, method = "pearson")

#salinity
salinityH = ggplot(aes(x = sal_avg, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Salinity")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14), 
        legend.position = "none")
cor(ecometrics$sal_avg, ecometrics$avg_spl_high, method = "pearson")

#depth
depthH = ggplot(aes(x = depth_m_avg, y = avg_spl_high),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Depth")+
  #ylab("Average SPL (dB re 1 uPa)")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 14), 
        legend.position = "none")
cor(ecometrics$depth_m_avg, ecometrics$avg_spl_high, method = "pearson")


#grid.arrange(oysterH, richnessH, totalHabH,tempH, salinityH, depthH, nrow = 2,ncol = 3)
grid.arrange(diversityH, richnessH, totalCoverH, oysterPerimH, soniferousSH, deployH,tempH, salinityH, depthH, nrow = 3)

```

# Toadfish

```{r}

#richness comb
richnessT = ggplot(aes(x = richness_comb, y = TFAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat Richness")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$richness_comb, ecometrics$TFAvgPresentNight, method = "pearson")

# total cover
totalCoverT = ggplot(aes(x = total_cover, y = TFAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Total habitat cover")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$total_cover, ecometrics$TFAvgPresentNight, method = "pearson")

#oyster core area
oysterCoreAreaT = ggplot(aes(x = oyster_core.area, y = TFAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Oyster core area")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$oyster_core.area, ecometrics$TFAvgPresentNight, method = "pearson")

# seagrass_perimeter
seagrassPerimT = ggplot(aes(x = seagrass_perimeter, y = TFAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Seagrass Perimeter")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$seagrass_perimeter, ecometrics$TFAvgPresentNight, method = "pearson")

# habitat_total
habitatTotalT = ggplot(aes(x = habitat_total, y = TFAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Total habitat area")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$habitat_total, ecometrics$TFAvgPresentNight, method = "pearson")

# carnivore
carnivoreT = ggplot(aes(x = carnivore, y = TFAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Carnivore CPUE")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$carnivore, ecometrics$TFAvgPresentNight, method = "pearson")

# deploy_num
deployT = ggplot(aes(x = deploy_num, y = TFAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Deployment")+
  #ylab("Toadfish Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$deploy_num, ecometrics$TFAvgPresentNight, method = "pearson")


grid.arrange(richnessT, totalCoverT,  oysterCoreAreaT, seagrassPerimT, habitatTotalT, carnivoreT, deployT, ncol = 3)

## Summary of toadfish call rates
toadfish_rates = ecometrics %>%
  select(site, habitat,deploy_num,TFAvgPresentNight) %>%
  filter(ToadCallRate > 0)

min(toadfish_rates$TFAvgPresentNight)
max(toadfish_rates$TFAvgPresentNight)
unique(toadfish_rates$habitat)
unique(toadfish_rates$deploy_num)


```

# Silver Perch

```{r}

# richness
richnessP = ggplot(aes(x = richness , y = PerchAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat species richness")+
  #ylab("Silver perch Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$richness, ecometrics$PerchAvgPresentNight, method= "pearson")

# shannonD
shannonDP = ggplot(aes(x = shannonD, y = PerchAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat diversity")+
  #ylab("Silver perch Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$shannonD, ecometrics$PerchAvgPresentNight, method= "pearson")

# seagrass
seagrassP = ggplot(aes(x = seagrass, y = PerchAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Total seagrass cover")+
  #ylab("Silver perch Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$seagrass, ecometrics$PerchAvgPresentNight, method= "pearson")

# richness_comb
richness_combP = ggplot(aes(x = richness_comb, y = PerchAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Habitat type richness")+
  #ylab("Silver perch Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$richness_comb, ecometrics$PerchAvgPresentNight, method= "pearson")

# seagrass_core_area
seagrassCoreAreaP = ggplot(aes(x = seagrass_core.area, y = PerchAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Seagrass core area")+
  #ylab("Silver perch Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$seagrass_core.area, ecometrics$PerchAvgPresentNight, method= "pearson")

# dist2adjPatch
dist2adjPatchP = ggplot(aes(x = dist2adjPatch, y = PerchAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Patch Isolation")+
  #ylab("Silver perch Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$dist2adjPatch, ecometrics$PerchAvgPresentNight, method= "pearson")
# pos relationship is even stronger when MA (outlier) is removed
perchIsolation = ecometrics$dist2adjPatch
perchIsolation[12] = NA
perchRate = ecometrics$PerchAvgPresentNight
perchRate[12] = NA
cor(perchIsolation,perchRate, method = "pearson", use = "complete.obs")

# comm_shannonD_sum
comm_shannonDP = ggplot(aes(x = comm_shannonD_sum, y = PerchAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Community diversity")+
  #ylab("Silver perch Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$comm_shannonD_sum, ecometrics$PerchAvgPresentNight, method= "pearson")

# avgTempNight
avgTempP = ggplot(aes(x = avgTempNight, y = PerchAvgPresentNight),data = ecometrics)+ theme_bw()+
  geom_point(aes(color = habitat))+
  geom_smooth(method = "lm", formula = 'y ~x', se = FALSE, color = "black")+
  xlab("Average Temperature")+
  #ylab("Silver perch Call Rate")+
  ylab(NULL)+
  theme(axis.title = element_text(size = 16), 
        axis.text = element_text(size = 16),
        legend.position = "none")
cor(ecometrics$avgTempNight, ecometrics$PerchAvgPresentNight, method= "pearson")

grid.arrange(richnessP, shannonDP, seagrassP, richness_combP, seagrassCoreAreaP, dist2adjPatchP, comm_shannonDP, avgTempP, ncol = 4)

```

## Modeling Low frequency SPL

```{r}

# This currently doesn't account for habitat type - which likely confounds some trends
metricModP = lm(avg_spl_low ~ halodule + ruppia + richness, data = ecometrics)
metricModL = lm(avg_spl_low ~ seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter, data = ecometrics)
metricModC = lm(avg_spl_low ~ comm_shannonD_sum + num_bai_chr, data = ecometrics)
metricModA = lm(avg_spl_low ~ avg_temp, data = ecometrics)
metricModPL = lm(avg_spl_low ~ halodule + ruppia + richness +  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter,
                 data = ecometrics)
metricModPC = lm(avg_spl_low ~ halodule + ruppia + richness + comm_shannonD_sum + num_bai_chr, data = ecometrics)
metricModPA = lm(avg_spl_low ~ halodule + ruppia + richness + avg_temp, data = ecometrics)
metricModLC = lm(avg_spl_low ~  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter + comm_shannonD_sum + num_bai_chr, data = ecometrics)
metricModLA = lm(avg_spl_low ~  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter + avg_temp, data = ecometrics)
metricModCA = lm(avg_spl_low ~ comm_shannonD_sum + num_bai_chr + avg_temp, data = ecometrics)
metricModPLC = lm(avg_spl_low ~ halodule + ruppia + richness +  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter
                  + comm_shannonD_sum + num_bai_chr, data = ecometrics)
metricModPLA = lm(avg_spl_low ~ halodule + ruppia + richness +  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter
                  + avg_temp, data = ecometrics)
metricMODPCA = lm(avg_spl_low ~ halodule + ruppia + richness + comm_shannonD_sum + num_bai_chr + avg_temp, data = ecometrics)
metricModLCA = lm(avg_spl_low ~  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter + comm_shannonD_sum + num_bai_chr + avg_temp,
                  data = ecometrics)
metricModPLCA = lm(avg_spl_low ~ halodule + ruppia + richness +  seagrass_core.area + seagrass_perim.area.ratio + oyster_perimeter
                  + comm_shannonD_sum + num_bai_chr + avg_temp, data = ecometrics)

model.sel(metricModPLCA, metricModLCA, metricMODPCA, metricModPLA, metricModPLC, metricModCA, metricModLA, metricModLC,
    metricModPA, metricModPC, metricModPL, metricModP, metricModL, metricModC, metricModA)

# PLA, PL, C, LA, CA are all indiscernible by AICc
# AICc is a correction for small sample size - should likely use here. 

LowFMods = list(metricModPLA, metricModPL, metricModC, metricModLA, metricModCA)
importance(LowFMods)
# Do not include community

# Variance Partitioning
Lpatch = summary(metricModPLA)$r.squared - summary(metricModLA)$r.squared
Llandscape = summary(metricModPLA)$r.squared - summary(metricModPA)$r.squared
Labiotic = summary(metricModPLA)$r.squared - summary(metricModPL)$r.squared
Lunexplained = 1 - summary(metricModPLA)$r.squared
Ltotal = summary(metricModPLA)$r.squared

```

## Modeling High frequency SPL

```{r}
HmetricModP = lm(avg_spl_low ~ shannonD + richness_comb + total_cover , data = ecometrics)
HmetricModL = lm(avg_spl_low ~ oyster_perimeter, data = ecometrics)
HmetricModC = lm(avg_spl_low ~ soniferous_S, data = ecometrics)
HmetricModA = lm(avg_spl_low ~ deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)
HmetricModPL = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + oyster_perimeter, data = ecometrics)
HmetricModPC = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + soniferous_S, data = ecometrics)
HmetricModPA = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)
HmetricModLC = lm(avg_spl_low ~ oyster_perimeter + soniferous_S, data = ecometrics)
HmetricModLA = lm(avg_spl_low ~ oyster_perimeter + deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)
HmetricModCA = lm(avg_spl_low ~ soniferous_S + deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)
HmetricModPLC = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + oyster_perimeter + soniferous_S, data = ecometrics)
HmetricModPLA = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + oyster_perimeter
                  + deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)
HmetricModPCA = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + soniferous_S + deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)
HmetricModLCA = lm(avg_spl_low ~ oyster_perimeter + soniferous_S + deploy_num + avg_temp + depth_m_avg + sal_avg,
                  data = ecometrics)
HmetricModPLCA = lm(avg_spl_low ~ shannonD + richness_comb + total_cover  + oyster_perimeter
                  + soniferous_S + deploy_num + avg_temp + depth_m_avg + sal_avg, data = ecometrics)

model.sel(HmetricModPLCA, HmetricModLCA, HmetricModPCA, HmetricModPLA, HmetricModPLC, HmetricModCA, HmetricModLA, HmetricModLC,
    HmetricModPA, HmetricModPC, HmetricModPL, HmetricModP, HmetricModL, HmetricModC, HmetricModA)

# within 2 AIC
# AICc: PL & PLC
# AIC: PLC, PLCA, PLA, & PL 

# Variable importance
HighFMods = list(HmetricModPL, HmetricModPLC)
importance(HighFMods)

# Variance partitioning High Frequency:
# the math is correct there are negative shared variances - look into more to understand
Hpatch = summary(HmetricModPLC)$r.squared - summary(HmetricModLC)$r.squared
Hlandscape = summary(HmetricModPLC)$r.squared - summary(HmetricModPC)$r.squared
Hcommunity = summary(HmetricModPLC)$r.squared - summary(HmetricModPL)$r.squared
Hunexplained = 1- summary(HmetricModPLC)$r.squared
Htotal = summary(HmetricModPLC)$r.squared

# sum of unique explanation is greater than the total?? something seems wrong there
# negative shared variance
Htotal_explained = summary(HmetricModPLC)$r.squared
H_patch + H_landscape + H_comm

# Allen advises against variance partitioning with more than three categories - 
# can use variable weights from AIC to justify which metric categories should be included. 
```

### Modeling toadfish

```{r}

TmetricModP = lm(TFAvgPresentNight ~ richness_comb + total_cover, data = ecometrics)
TmetricModL = lm(TFAvgPresentNight ~ oyster_core.area + seagrass_perimeter + habitat_total, data = ecometrics)
TmetricModC = lm(TFAvgPresentNight ~ carnivore, data = ecometrics)
TmetricModA = lm(TFAvgPresentNight ~ deploy_num, data = ecometrics)
TmetricModPL = lm(TFAvgPresentNight ~ richness_comb + total_cover + oyster_core.area + seagrass_perimeter + habitat_total, data = ecometrics)
TmetricModPC = lm(TFAvgPresentNight ~ richness_comb + total_cover + carnivore, data = ecometrics)
TmetricModPA = lm(TFAvgPresentNight ~ richness_comb + total_cover + deploy_num, data = ecometrics)
TmetricModLC = lm(TFAvgPresentNight ~ oyster_core.area + seagrass_perimeter + habitat_total + carnivore, data = ecometrics)
TmetricModLA = lm(TFAvgPresentNight ~ oyster_core.area + seagrass_perimeter + habitat_total + deploy_num, data = ecometrics)
TmetricModCA = lm(TFAvgPresentNight ~ carnivore + deploy_num, data = ecometrics)
TmetricModPLC = lm(TFAvgPresentNight ~ richness_comb + total_cover + oyster_core.area + seagrass_perimeter + habitat_total + carnivore, data = ecometrics)
TmetricModPLA = lm(TFAvgPresentNight ~ richness_comb + total_cover + oyster_core.area + seagrass_perimeter + habitat_total + deploy_num, data = ecometrics)
TmetricModPCA = lm(TFAvgPresentNight ~ richness_comb + total_cover + carnivore + deploy_num, data = ecometrics)
TmetricModLCA = lm(TFAvgPresentNight ~ oyster_core.area + seagrass_perimeter + habitat_total + carnivore + deploy_num, data = ecometrics)
TmetricModPLCA = lm(TFAvgPresentNight ~ richness_comb + total_cover + oyster_core.area + seagrass_perimeter + habitat_total + carnivore + deploy_num, 
                    data = ecometrics)

model.sel(TmetricModPLCA, TmetricModLCA, TmetricModPCA, TmetricModPLA, TmetricModPLC, TmetricModCA, TmetricModLA, TmetricModLC,
    TmetricModPA, TmetricModPC, TmetricModPL, TmetricModP, TmetricModL, TmetricModC, TmetricModA)

#AICc: PA, PLA

# Calculate variable weights and decide whether to include landscape variables
ToadfishMods = list(TmetricModPA, TmetricModPLA)
importance(ToadfishMods)

# Attempting variance partitioning 
Tpatch = summary(TmetricModPLA)$r.squared - summary(TmetricModLA)$r.squared
Tlandscape = summary(TmetricModPLA)$r.squared - summary(TmetricModPA)$r.squared
Tabiotic = summary(TmetricModPLA)$r.squared - summary(TmetricModPL)$r.squared
Tunexplained = 1 - summary(TmetricModPLA)$r.squared
Ttotal = summary(TmetricModPLA)$r.squared 
Tpatch+Tlandscape+Tabiotic+Tunexplained

```

### Modeling Silver Perch

```{r}

PmetricModP = lm(PerchAvgPresentNight ~ richness + shannonD + seagrass + richness_comb, data = ecometrics)
PmetricModL = lm(PerchAvgPresentNight ~ seagrass_core.area + dist2adjPatch, data = ecometrics)
PmetricModC = lm(PerchAvgPresentNight ~ comm_shannonD_sum, data = ecometrics)
PmetricModA = lm(PerchAvgPresentNight ~ avgTempNight, data = ecometrics)
PmetricModPL = lm(PerchAvgPresentNight ~ richness + shannonD + seagrass + richness_comb + seagrass_core.area + dist2adjPatch, data = ecometrics)
PmetricModPC = lm(PerchAvgPresentNight ~ richness + shannonD + seagrass + richness_comb + comm_shannonD_sum, data = ecometrics)
PmetricModPA = lm(PerchAvgPresentNight ~ richness + shannonD + seagrass + richness_comb + avgTempNight, data = ecometrics)
PmetricModLC = lm(PerchAvgPresentNight ~ seagrass_core.area + dist2adjPatch + comm_shannonD_sum, data = ecometrics)
PmetricModLA = lm(PerchAvgPresentNight ~ seagrass_core.area + dist2adjPatch + avgTempNight, data = ecometrics)
PmetricModCA = lm(PerchAvgPresentNight ~ comm_shannonD_sum + avgTempNight, data = ecometrics)
PmetricModPLC = lm(PerchAvgPresentNight ~ richness + shannonD + seagrass + richness_comb + seagrass_core.area + dist2adjPatch + comm_shannonD_sum, 
                   data = ecometrics)
PmetricModPLA = lm(PerchAvgPresentNight ~ richness + shannonD + seagrass + richness_comb + seagrass_core.area + dist2adjPatch + avgTempNight, data = ecometrics)
PmetricModPCA = lm(PerchAvgPresentNight ~ richness + shannonD + seagrass + richness_comb + comm_shannonD_sum + avgTempNight, data = ecometrics)
PmetricModLCA = lm(PerchAvgPresentNight ~ seagrass_core.area + dist2adjPatch + comm_shannonD_sum + avgTempNight, data = ecometrics)
PmetricModPLCA = lm(PerchAvgPresentNight ~ richness + shannonD + seagrass + richness_comb + seagrass_core.area + dist2adjPatch + 
                      comm_shannonD_sum + avgTempNight, data = ecometrics)

model.sel(PmetricModPLCA, PmetricModLCA, PmetricModPCA, PmetricModPLA, PmetricModPLC, PmetricModCA, PmetricModLA, PmetricModLC,
    PmetricModPA, PmetricModPC, PmetricModPL, PmetricModP, PmetricModL, PmetricModC, PmetricModA)

# No need for variable importance when only 1 best model is identified

Plandscape = summary(PmetricModLA)$r.squared - summary(PmetricModA)$r.squared
Pabiotic = summary(PmetricModLA)$r.squared - summary(PmetricModL)$r.squared
Punexplained = 1 - summary(PmetricModLA)$r.squared
Ptotal = summary(PmetricModLA)$r.squared


```


