<<<<<<< HEAD
---
title: "TransmissionLossExp"
author: "Becca Van Hoeck"
date: "12/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages and data

```{r}

library(dplyr)
library(tidyr)
library(ggplot2)

signals = read.csv("data/sound_exp/signalSPLdata.csv", header = TRUE)

```

## Tidy data

```{r}

# group by site, frequency, distance, then calc mean spl

meanSPL = signals %>%
  group_by(site, frequency, distance) %>%
  summarize(meanSPL = mean(spl1,spl2,spl3,spl4,spl5,spl6,spl7,spl8,spl9,spl10))


Tloss = meanSPL %>%
  group_by(site,frequency) %>%
  summarize(TL0 = meanSPL)


```

# Cheat with excel TL quick and dirty summary

```{r}

signals$signalF = signals$frequency

# What do I use as the y? 
# do I need to change to long form?
#ggplot(data = signals, aes(x = distance))



tLoss = as.data.frame(read.csv("data/sound_exp/signalTLdata.csv", header = TRUE))

tLoss$site = factor(tLoss$site)
tLoss$distance = factor(tLoss$distance)
tLoss$frequency = factor(tLoss$frequency)
STdistance = tLoss$distance
tLoss$signalF = tLoss$frequency

ggplot(data = tLoss, aes(x = STdistance, y = meanTL, color = site))+ theme_bw()+
  geom_point()+
  geom_smooth()+
  facet_wrap(facets = signalF)


distance

```




=======
---
title: "TransmissionLossExp"
author: "Becca Van Hoeck"
date: "12/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages and data

```{r}

library(dplyr)
library(tidyr)
library(ggplot2)

signals = read.csv("data/sound_exp/signalSPLdata.csv", header = TRUE)

```

## Tidy data

```{r}

# group by site, frequency, distance, then calc mean spl

meanSPL = signals %>%
  group_by(site, frequency, distance) %>%
  summarize(meanSPL = mean(spl1,spl2,spl3,spl4,spl5,spl6,spl7,spl8,spl9,spl10))


Tloss = meanSPL %>%
  group_by(site,frequency) %>%
  summarize(TL0 = meanSPL)


```

# Cheat with excel TL quick and dirty summary

```{r}

signals$signalF = signals$frequency

# What do I use as the y? 
# do I need to change to long form?
#ggplot(data = signals, aes(x = distance))



tLoss = as.data.frame(read.csv("data/sound_exp/signalTLdata.csv", header = TRUE))

tLoss$site = factor(tLoss$site)
tLoss$distance = factor(tLoss$distance)
tLoss$frequency = factor(tLoss$frequency)
STdistance = tLoss$distance
tLoss$signalF = tLoss$frequency

ggplot(data = tLoss, aes(x = STdistance, y = meanTL, color = site))+ theme_bw()+
  geom_point()+
  geom_smooth()+
  facet_wrap(facets = signalF)


distance

```




>>>>>>> d69924ce5234437194dd03e3a9ca0fe3c6728deb
